---
title: "Bike Details"
format:
  html:
    toc: false
    theme: cosmo
params:
  brand: ""
  model: ""
  year: ""
  slug: ""
  data_path: "data/geobike.rds"
  site_base_url: "https://thegravelbikegeometryproject.com"
freeze: auto
---

```{r setup, include=FALSE}
library(data.table)
library(jsonlite)
library(knitr)

# Load data
geobike <- readRDS(params$data_path)

# Subset this bike
bike <- geobike[brand == params$brand & model == params$model & year == params$year]
if (nrow(bike) == 0) stop(sprintf("No rows found for: %s %s %s", params$brand, params$model, params$year))

# SEO strings
page_title <- sprintf("%s %s %s Geometry & Specs", params$brand, params$model, params$year)
page_desc  <- sprintf("Geometry, specs, and sizing for the %s %s (%s) gravel bike.",
                      params$brand, params$model, params$year)
canonical_url <- sprintf("%s/bikes/%s.html", params$site_base_url, params$slug)

# Optional image column
img_url <- if ("image_url" %in% names(bike)) bike[1, image_url] else NA_character_
```

```{r meta, echo=FALSE, results='asis'}
# Emit canonical + meta description as literal HTML (safe, minimal)
cat(sprintf('<link rel="canonical" href="%s">\n', canonical_url))
cat(sprintf('<meta name="description" content="%s">\n', page_desc))
# Also set browser title so tab shows the SEO title
cat(sprintf('<script>document.title=%s;</script>\n', toJSON(page_title, auto_unbox=TRUE)))
```

# `r page_title`

**Brand:** `r params$brand`  
**Model:** `r params$model`  
**Year:** `r params$year`  
**Category:** Gravel Bike

```{r hero, echo=FALSE, results='asis'}
if (!is.na(img_url) && nzchar(img_url)) {
  cat(sprintf(
    '<img src="%s" alt="%s %s %s" style="max-width:720px;width:100%%;border-radius:12px;margin:1rem 0;">',
    img_url, params$brand, params$model, params$year
  ))
}
```

## Geometry & Specs (static, crawlable)

```{r table, echo=FALSE}
keep_cols <- intersect(c(
  "size","reach","stack","top_tube_effective","seat_tube","head_tube",
  "head_tube_angle","seat_tube_angle","bb_drop","chainstay","wheelbase",
  "fork_offset","fork_axle_to_crown","trail","tire_width_max_700c",
  "tire_width_max_650b","handlebar","material","udh","stealth_dropper",
  "base_build_usd","frameset_usd"
), names(bike))

# Order by numeric size where possible
ord <- order(
  ifelse(is.na(bike$size), 999, suppressWarnings(as.numeric(gsub("[^0-9.]", "", bike$size)))),
  na.last = TRUE
)
kb <- bike[ord, ..keep_cols]

kable(kb, format = "html", table.attr = 'class="table table-sm table-striped"')
```

## Summary

- The **`r params$brand` `r params$model` (`r params$year`)** is listed in our gravel database with the geometry and specs above.  
- Looking for more? See **[all bikes index](/bikes/index.html)**.

### Related

- Explore other **`r params$brand`** models via our brand pages or the site index.  
- Compare **reach vs. stack** and **HTA vs. STA** in our interactive dashboards.

```{r jsonld, echo=FALSE, results='asis'}
first_row <- if (nrow(kb)) as.list(kb[1]) else list()
props <- lapply(names(first_row), function(nm) {
  list(`@type`="PropertyValue", name=nm, value=as.character(first_row[[nm]]))
})

schema <- list(
  `@context` = "https://schema.org",
  `@type`    = "Product",
  name       = sprintf("%s %s %s", params$brand, params$model, params$year),
  brand      = list(`@type`="Brand", name=params$brand),
  category   = "Bicycle",
  productID  = paste(params$brand, params$model, params$year),
  url        = canonical_url,
  image      = if (is.na(img_url) || !nzchar(img_url)) NULL else img_url,
  description= page_desc,
  additionalProperty = props
)

cat('<script type="application/ld+json">')
cat(toJSON(schema, auto_unbox = TRUE, null = "null"))
cat('</script>')
```

**Internal Links:**  
- [All bikes index](/bikes/index.html)  
- [Home](/)
