---
title: "How does a suspension fork change bike geometry?"
subtitle: "And how race/rowdy/relaxed are they?"
---

```{r gravel-sus-setup, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)

```


```{r geom-table, echo=FALSE, eval=TRUE}
library(DT)

row_i <- 573 # sklar ML
table_cols <- c("axle_crown", "stack", "reach", "head_tube_angle", "seat_tube_angle", "bottom_bracket_drop", "wheelbase", "front_center", "rear_center", "trail")


geom_table <- data.table(NULL)

#for(row_i in 1:nrow(geobike)){
for(row_i in 1:nrow(geobike)){
  rigid <- geobike[row_i, .SD, .SDcols = table_cols] |> as.numeric()
  rudy_30_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "30 45")] |> as.numeric()
  rudy_30_51 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "30 51")] |> as.numeric()
  rudy_40_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "40 45")] |> as.numeric()
  rudy_40_51 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "40 51")] |> as.numeric()
  
  geom_table <- rbind(
    geom_table,
    data.table(
      Model = geobike[row_i, model_size],
      Measure = table_cols,
      Rigid = as.integer(rigid),
      "Travel = 30, Offset = 45" = as.integer(rudy_30_45),
      "Travel = 40, Offset = 45" = as.integer(rudy_40_45),
      "Travel = 30, Offset = 51" = as.integer(rudy_30_51),
      "Travel = 40, Offset = 51" = as.integer(rudy_40_51)
    ))
}

header_list <- names(geom_table)[-1]
n_col <- ncol(geom_table)
data_matrix <- t(as.matrix(unname(geom_table)))

geom_table_shared <- SharedData$new(geom_table, group = "model_group")

fig <- datatable(geom_table_shared,
                 options = list(autoWidth = TRUE))

filter_ui <- filter_select(id = "fsid", 
                         label = "Model", 
                         sharedData = geom_table_shared, 
                         group = ~Model,
                         multiple = FALSE)


 p <- bscols(widths = c(2, 10), filter_ui, fig
  )
  
  p



```


```{r echo=FALSE, eval=FALSE}

library(plotly)
library(crosstalk)
library(DT)
library(htmltools)

df <- data.frame(
  Model = c("A", "B", "A", "C", "B", "C"),
  Value = c(10, 20, 15, 30, 25, 35)
)

# Create shared data
geom_table_shared <- SharedData$new(df, group = "model_group")

# Dropdown filter
filter_ui <- filter_select(
  id = "fsid", 
  label = "Model", 
  sharedData = geom_table_shared, 
#  group = "model_group",
  group = ~Model,
  multiple = FALSE
)

# Crosstalk-friendly table
fig <- datatable(geom_table_shared)

# Layout
bscols(widths = c(3, 9), filter_ui, fig)
```



::: {.callout-tip title="Which bikes are racy? rowdy? relaxed?"}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model in the plot.
3. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-note}
1. The ternary scores are the projections of the centered, scaled data onto the style (Racy, Relaxed, Rowdy) axes.
2. There are several ways to construct a style axis. The ternary plot uses the 2nd of these two ways:
    i. the vector of differences from the centroid to the style mean of the centered, scaled data.
    ii. the vector of correlation coefficients between the style classification (1 is "in style" and 0 is "out of style") and each measure.
3. The input data is the ML subset of bikes that fit a 176 cm rider
:::

