---
title: "Gravel Ternary"
---

```{r gravel-ternary-setup, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)

```


```{r legend, echo=FALSE, fig.width= 8, fig.height=0.5}
#| fig-height: 1
gg <- ggplot(data = geobike,
       aes(x = reach,
           y = stack,
           color = restyle)) +
  geom_point() +
  scale_color_manual(name = "Classification",
                     values = pal_okabe_ito_3) +
  theme_pubr() +
  theme(legend.position="top") +
  NULL
  
gg_legend <- get_legend(gg)
plot_grid(gg_legend)

```


```{r ternary-plot, echo=FALSE, out.width = "100%", out.height = "100%"}
p <- base_ternary(my_fit)
p
```


::: {.callout-tip}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model in the plot.
3. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-note}
1. The ternary scores are the projections of the centered, scaled data onto the style (Racy, Relaxed, Rowdy) axes.
2. Each style axes was constructed as the multivariate axis from the centroid to the style mean of the centered, scaled data.
3. The input data is the ML subset of bikes that fit a 176 cm rider
:::

