---
title: "Gravel 2D"
editor: source
format:
  html:
    toc: false
---
::: {.callout-tip}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model and frame size combinations.
3. Click on **Focal** checkbox to view the frame size used for the classification.
4. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 176 cm (5' 9.3") high rider, according to manufacturer's charts.
:::


```{r setup-gravel-scatter, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```

```{r legend, echo=FALSE, fig.width= 8, fig.height=0.5}
# plot_ly(data = geobike, type = "scatter", mode = "markers",
#         x = ~ reach,
#         y = ~ stack,
#         color = ~restyle,
#         colors = my_palette,
#         size = 10,
#         visible = "legendonly"
# )
#| fig-height: 1
gg <- ggplot(data = geobike,
       aes(x = reach,
           y = stack,
           color = restyle)) +
  geom_point() +
  scale_color_manual(name = "Classification",
                     values = pal_okabe_ito_3) +
  theme_pubr() +
  theme(legend.position="top") +
  NULL
  
gg_legend <- get_legend(gg)
plot_grid(gg_legend)

```

```{r, warning=FALSE, message=FALSE, echo=FALSE, out.width = "90%", out.height = "90%"}

p1 <- scatter_fig_new(data = geobike,
                  x_col = "reach", y_col = "stack",
                  x_label = "Reach (mm)", y_label = "Stack (mm)")
p2 <- scatter_fig_new(data = geobike,
                  x_col = "top_tube_effective_length",
                  y_col = "chainstay_length",
                  x_label = "TT Effective Length (mm)",
                  y_label = "Chainstay Length (mm)",
                  x_info = "ETT", y_info = "CS")
p3 <- scatter_fig_new(data = geobike,
                  x_col = "front_center", y_col = "rear_center",
                  x_label = "Front Center (mm)", y_label = "Rear Center (mm)",
                  x_info = "FC", y_info = "RC")
p4 <- scatter_fig_new(data = geobike,
                  x_col = "seat_tube_angle", y_col = "head_tube_angle",
                  x_label = "Seat Tube Angle (째)", y_label = "Head Tube Angle (째)",
                  x_info = "STA", y_info = "HTA", digits = 1)
p5 <- scatter_fig_new(data = geobike,
                  x_col = "seat_tube_length", y_col = "top_tube_angle",
                  x_label = "Seat Tube Length (mm)", y_label = "Top Tube Angle (째)",
                  x_info = "STL", y_info = "TTA", digits = 1,
                  same_xy_scale = FALSE)
p6 <- scatter_fig_new(data = geobike,
                  x_col = "head_tube_angle", y_col = "trail",
                  x_label = "Head Tube Angle (째)", y_label = "Trail (mm)",
                  x_info = "HTA", y_info = "Trail", digits = 1,
                  same_xy_scale = FALSE)
p7 <- scatter_fig_new(data = geobike,
                  x_col = "front_wheelbase", y_col = "stack_reach",
                  x_label = "Front Center/Wheelbase", y_label = "Stack/Reach",
                  x_info = "FC/WB", y_info = "Stack/Reach", digits = 2,
                  same_xy_scale = FALSE)
p8 <- scatter_fig_new(data = geobike,
                  x_col = "front_wheelbase", y_col = "sta_hta",
                  x_label = "Front Center/Wheelbase", y_label = "STA/HTA",
                  x_info = "FC/WB", y_info = "STA/HTA", digits = 2,
                  same_xy_scale = FALSE)

### Stack vs. Reach
### Chainstay Length vs. Effective top tube length
### Rear Center vs. Front Center
### Head Tube Angle vs. Seat Tube Angle
### Top Tube Angle vs. Seat Tube Angle
### Trail vs. Head Tube Angle
### Stack/Reach vs. Front Center/Wheelbase
### Seat Tube Angle/Head Tube Angle vs. Front Center/Wheelbase

```



```{r, warning=FALSE, message=FALSE, echo=FALSE, out.width="80%"}
p1
p2
p3
p4
p5
p6
p7

```


