---
title: "Gravel Tree"
editor: source
---

::: {.callout-note}
1. The tree was computed using [Ward's hierarchical clustering method](https://en.wikipedia.org/wiki/Ward%27s_method){target="_blank"}.
2. The tree is based on a frame size that fits a 175 cm high rider (generally frame size M or 54), according to manufacturer's charts. Splitting the tree into the three major clusters results in a classification that is close to, but not equivalent, to the classification computed using robust k-means (the classification elsewhere on this site).
:::

```{r setup-tree, warning=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      knitr.kable.NA = '')

source_path <- here::here("bike_geometry_project.R")
source(source_path)

```

```{r gravel-tree, fig.height=14, fig.width=10, echo=FALSE}

tree_path <- here("rds", "tree.Rds")
tree_v2_color <- readRDS(tree_path)

gg <- plot_ggdendro(tree_v2_color,
                      direction   = "lr",
                      expand.y    = 0.4,
                      scale.color = pal_okabe_ito_3[c(1,3,2)])
 
gg
```

```{r gravel-tree-explore, fig.height=14, fig.width=10, echo=FALSE, eval=FALSE}
tree_v2_color_explore <- dendro_data_k(tree_v2, k = 5)

gg <- plot_ggdendro(tree_v2_color_explore,
                      direction   = "lr",
                      expand.y    = 0.4,
                      scale.color = pal_okabe_ito)
 
gg

```

```{r echo=FALSE, eval = FALSE,fig.height=14, fig.width=10, echo=FALSE}
inc_cols <-  c("stack", "reach", "front_center", "rear_center",
               "head_tube_angle", "seat_tube_angle",
               "trail",
               "seat_tube_length",
#               "top_tube_angle",
               NULL)

tree_wardd2 <- get_tree(my_fit,
                        inc_cols,
                        scale_it = TRUE,
                        center_it = TRUE,
                        hclust_method = "ward.D2") # "average" "ward.D2"
tree_upgma <- get_tree(my_fit,
                        inc_cols,
                        scale_it = TRUE,
                        center_it = TRUE,
                        hclust_method = "average") # "average" "ward.D2"
# dend1 <- as.dendrogram(tree_v2)
#plot_dendro(dend1, width = 1200, height = 2000)
k = 3
tree_wardd2_color <- dendro_data_k(tree_wardd2, k = k)
plot_ggdendro(tree_wardd2_color,
              direction   = "lr",
              expand.y    = 0.4,
              scale.color = pal_okabe_ito_7[1:k])

k = 5
tree_upgma_color <- dendro_data_k(tree_upgma, k = k)
plot_ggdendro(tree_upgma_color,
              direction   = "lr",
              expand.y    = 0.4,
              scale.color = pal_okabe_ito_7[1:k])



```

