---
title: "Gravel 2D"
editor: source
format:
  html:
    toc: false
---
::: {.callout-tip}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model and frame size combinations.
3. Click on **Focal** checkbox to view only the frame size used for the classification.
4. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 176 cm (5' 9.3") high rider, according to manufacturer's charts.
:::

[Click here to see a version of this page that simultaneously highlights all frame sizes within a model](../qmd/gravel_scatter_model.qmd)

```{r setup-gravel-scatter, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```


```{r plot-headers, warning=FALSE, message=FALSE, eval=FALSE, echo=FALSE, out.width = "90%", out.height = "90%"}

### Stack vs. Reach
### Chainstay Length vs. Effective top tube length
### Rear Center vs. Front Center
### Head Tube Angle vs. Seat Tube Angle
### Top Tube Angle vs. Seat Tube Angle
### Trail vs. Head Tube Angle
### Stack/Reach vs. Front Center/Wheelbase
### Seat Tube Angle/Head Tube Angle vs. Front Center/Wheelbase

```

```{r make-plots, echo=FALSE}

geobike_shared <- SharedData$new(geobike, key = ~model_size, group = "2dscatter")

p1 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "reach", y_col = "stack",
                  x_label = "Reach (mm)", y_label = "Stack (mm)",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p2 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_center", y_col = "rear_center",
                  x_label = "Front Center (horizontal) (mm)", y_label = "Rear Center (horizontal) (mm)",
                  x_info = "FC", y_info = "RC",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p3 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "wheelbase", y_col = "bottom_bracket_drop",
                  x_label = "Wheelbase (mm)", y_label = "Bottom Bracket Drop (mm)",
                  x_info = "WB", y_info = "BB drop",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p4 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "seat_tube_angle", y_col = "head_tube_angle",
                  x_label = "Seat Tube Angle (°)", y_label = "Head Tube Angle (°)",
                  x_info = "STA", y_info = "HTA", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p5 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "chainstay_length",
                  y_col = "seat_tube_length",
                  x_label = "Chainstay Length (mm)",
                  y_label = "Seat Tube Length (mm)",
                  x_info = "CS", y_info = "STL",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p6 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "seat_tube_length", y_col = "top_tube_angle",
                  x_label = "Seat Tube Length (mm)", y_label = "Top Tube Angle (°)",
                  x_info = "STL", y_info = "TTA", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p7 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "trail", y_col = "trail_45",
                  x_label = "Trail (mm)", y_label = "Trail (45 mm tire) (mm)",
                  x_info = "Trail", y_info = "Trail-45", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p8 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_wheelbase", y_col = "stack_reach",
                  x_label = "Front Center/Wheelbase", y_label = "Stack/Reach",
                  x_info = "FC/WB", y_info = "Stack/Reach", digits = 2,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p9 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_wheelbase", y_col = "sta_hta",
                  x_label = "Front Center/Wheelbase", y_label = "STA/HTA",
                  x_info = "FC/WB", y_info = "STA/HTA", digits = 2,
                  g_col = "model_size",
                  same_xy_scale = FALSE)


```


```{r, echo = FALSE, out.height="100%", out.width="100%"}
# set up check boxes

  # gg_legend_ly <- ggplotly(gg_legend, width = 6.5*96, height = 1*96)

  #boxes <- filter_checkbox("size", "Size", geobike_shared, ~Size, inline = FALSE)
  boxes <- filter_checkbox("size", "Size", geobike_shared, ~frame_size_std, inline = FALSE)

  bscols(widths = c(8,3), p1, boxes)
  bscols(widths = c(8,3), p2)
  bscols(widths = c(8,3), p3)
  bscols(widths = c(8,3), p4)
  bscols(widths = c(8,3), p5)
  bscols(widths = c(8,3), p6)
  bscols(widths = c(8,3), p7)
  bscols(widths = c(8,3), p8)
  bscols(widths = c(8,3), p9)

```



