---
title: "Gravel Style"
editor: source
format:
  html:
    toc: false
---
::: {.callout-tip}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model and frame size combinations.
3. Click on **Focal** checkbox to view only the frame size used for the classification.
4. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 176 cm (5' 9.3") high rider, according to manufacturer's charts.
:::

[Click here to see a version of this page that simultaneously highlights all frame sizes within a model](../qmd/gravel_scatter_model.qmd)

```{r setup-gravel-scatter, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```

```{r legend, echo=FALSE, eval=FALSE, fig.width= 8, fig.height=0.5}
# plot_ly(data = geobike, type = "scatter", mode = "markers",
#         x = ~ reach,
#         y = ~ stack,
#         color = ~restyle,
#         colors = my_palette,
#         size = 10,
#         visible = "legendonly"
# )
#| fig-height: 1
gg <- ggplot(data = geobike,
       aes(x = reach,
           y = stack,
           color = restyle)) +
  geom_point() +
  scale_color_manual(name = "Classification",
                     values = pal_okabe_ito_3) +
  theme_pubr() +
  theme(legend.position="top") +
  NULL
  
gg_legend <- get_legend(gg)
plot_grid(gg_legend)

```

```{r make-plots, echo=FALSE}

geobike_shared <- SharedData$new(geobike)

# which classifier
tree_class <- 1
functional_class <- 2
kmeans_class <- 3
mclust_class <- 4
racy_col <- c("tree_racy", "functional_racy", "kmeans_racy", "mclust_racy")[kmeans_class]
relaxed_col <- c("tree_relaxed", "functional_relaxed", "kmeans_relaxed", "mclust_relaxed")[kmeans_class]
rowdy_col <- c("tree_rowdy", "functional_rowdy", "kmeans_rowdy", "mclust_rowdy")[kmeans_class]
color_col <- c("tree_style", "functional_style", "kmeans_style", "mclust_style")[kmeans_class]

p1 <- scatter_fig_global(data = geobike_shared,
                  x_col = racy_col, y_col = rowdy_col,
                  x_label = "Raciness", y_label = "Rowdiness",
                  g_col = "model_size",
                  x_info = "Racy", y_info = "Rowdy",
                  same_xy_scale = FALSE)
p2 <- scatter_fig_global(data = geobike_shared,
                  x_col = rowdy_col, y_col = relaxed_col,
                  x_label = "Rowdiness", y_label = "Relaxedness",
                  x_info = "Rowdy", y_info = "Relaxed",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p3 <- scatter_fig_global(data = geobike_shared,
                  x_col = racy_col, y_col = relaxed_col,
                  x_label = "Raciness", y_label = "Relaxedness",
                  x_info = "Racy", y_info = "Relaxed",
                  g_col = "model_size",
                  same_xy_scale = FALSE)

```


```{r, echo = FALSE, out.height="100%", out.width="100%"}
# set up check boxes

  # gg_legend_ly <- ggplotly(gg_legend, width = 6.5*96, height = 1*96)

  #boxes <- filter_checkbox("size", "Size", geobike_shared, ~Size, inline = FALSE)
  boxes <- filter_checkbox("size", "Size", geobike_shared, ~frame_size_std, inline = FALSE)
  # boxes$attribs$style <- css(font.size = "90%") # <-change the font size

  p1_box <- bscols(
    widths = c(7,3,2), p1, boxes
  )
  
  p1_box
  p2
  p3
# cowplot::plot_grid(gg_legend, boxes)
```



