---
title: "Gravel Geometry"
editor: source
format:
  html:
    toc: false
---
::: {.callout-tip title="Tips for navigating"}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model and frame size combinations.
3. Click on Rider Height checkbox to view frames of a specific size. The 175 height is the most complete.
4. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-tip title="More notes!"}
More notes at the bottom!
:::


[Click here to see a version of this page that simultaneously highlights all frame sizes within a model](../qmd/gravel_scatter_model.qmd)

```{r setup-gravel-scatter, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```


```{r plot-headers, warning=FALSE, message=FALSE, eval=FALSE, echo=FALSE, out.width = "90%", out.height = "90%"}

### Stack vs. Reach
### Chainstay Length vs. Effective top tube length
### Rear Center vs. Front Center
### Head Tube Angle vs. Seat Tube Angle
### Top Tube Angle vs. Seat Tube Angle
### Trail vs. Head Tube Angle
### Stack/Reach vs. Front Center/Wheelbase
### Seat Tube Angle/Head Tube Angle vs. Front Center/Wheelbase

```

```{r size-stats, echo=FALSE, eval=FALSE}
sizes <- c("XXS", "XS", "S", "SM", "M", "ML", "L", "XL", "XXL")
median_min <- numeric(length(sizes))
median_max <- numeric(length(sizes))
median_val <- numeric(length(sizes))
for(i in 1:length(sizes)){
  median_min[i] <- median(geobike[frame_size_letters == sizes[i],
                                  rider_min], na.rm = TRUE)
  median_max[i] <- median(geobike[frame_size_letters == sizes[i],
                                  rider_max], na.rm = TRUE)
  median_val[i] <- median(c(median_min[i], median_max[i]), na.rm = TRUE)
}
size_chart <- data.table(
  size = sizes,
  rider_min = median_min,
  rider_max = median_max,
  rider_size = median_val
)
# top end of S

frame_size_list <- c("XXS", "XS", "XS/S", "S", "S/M", "M", "M/L", "L", "L/XL", "XL", "XXL")
rider_height_list <- c(153, 159, 163, 167, 171, 175, 179, 183, 187, 191, 196)
median_frame_size <- numeric(length(rider_height_list))
for(i in 1:length(number_list)){
  median_frame_size[i] <- median(geobike[rider_height_list[i] > rider_min & rider_height_list[i] <= rider_max, frame_size_numbers], na.rm = TRUE)
}
final_size_chart <- data.table(
  rider_height = rider_height_list,
  frame_size_char = frame_size_list,
  frame_size_num = median_frame_size
)

```

```{r make-plots, echo=FALSE}

geobike_shared <- SharedData$new(geobike, key = ~model_size, group = "2dscatter")

p1 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "reach", y_col = "stack",
                  x_label = "Reach (mm)", y_label = "Stack (mm)",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p2 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_center", y_col = "rear_center",
                  x_label = "Front Center (horizontal) (mm)", y_label = "Rear Center (horizontal) (mm)",
                  x_info = "FC", y_info = "RC",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p3 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "wheelbase", y_col = "bottom_bracket_drop",
                  x_label = "Wheelbase (mm)", y_label = "Bottom Bracket Drop (mm)",
                  x_info = "WB", y_info = "BB drop",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p4 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "seat_tube_angle", y_col = "head_tube_angle",
                  x_label = "Seat Tube Angle (°)", y_label = "Head Tube Angle (°)",
                  x_info = "STA", y_info = "HTA", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p5 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "chainstay_length",
                  y_col = "seat_tube_length",
                  x_label = "Chainstay Length (mm)",
                  y_label = "Seat Tube Length (mm)",
                  x_info = "CS", y_info = "STL",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p6 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "seat_tube_length", y_col = "top_tube_angle",
                  x_label = "Seat Tube Length (mm)", y_label = "Top Tube Angle (°)",
                  x_info = "STL", y_info = "TTA", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p7 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "trail", y_col = "trail_45",
                  x_label = "Trail (mm)", y_label = "Trail (45 mm tire) (mm)",
                  x_info = "Trail", y_info = "Trail-45", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p8 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_wheelbase", y_col = "stack_reach",
                  x_label = "Front Center/Wheelbase", y_label = "Stack/Reach",
                  x_info = "FC/WB", y_info = "Stack/Reach", digits = 2,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p9 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_wheelbase", y_col = "sta_hta",
                  x_label = "Front Center/Wheelbase", y_label = "STA/HTA",
                  x_info = "FC/WB", y_info = "STA/HTA", digits = 2,
                  g_col = "model_size",
                  same_xy_scale = FALSE)


```


```{r, echo = FALSE, out.height="100%", out.width="100%"}
# set up check boxes

  # gg_legend_ly <- ggplotly(gg_legend, width = 6.5*96, height = 1*96)

  #boxes <- filter_checkbox("size", "Size", geobike_shared, ~Size, inline = FALSE)
  sm_box <- filter_checkbox("small", "Small", geobike_shared, ~frame_size_std_s, inline = FALSE)
  med_box <- filter_checkbox("med", "Medium", geobike_shared, ~frame_size_std_m, inline = FALSE)
  lg_box <- filter_checkbox("large", "Large", geobike_shared, ~frame_size_std_l, inline = FALSE)
  height_boxes <- filter_checkbox("rider_height", "Rider Height", geobike_shared, ~frame_size_std_fine, inline = FALSE)


#  bscols(widths = c(8,1,1,1,1), p1, sm_box, med_box, lg_box, height_boxes)
  bscols(p1,
         list(sm_box, med_box, lg_box),
         height_boxes,
         widths = c(8, 2, 2))
  bscols(widths = c(8,4), p2)
  bscols(widths = c(8,4), p3)
  bscols(widths = c(8,4), p4)
  bscols(widths = c(8,4), p5)
  bscols(widths = c(8,4), p6)
  bscols(widths = c(8,4), p7)
  bscols(widths = c(8,4), p8)
  bscols(widths = c(8,4), p9)

```

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 175 cm high rider (generally frame size M or 54), according to manufacturer's charts.
:::

