---
title: "Gravel Geometry"
editor: source
format:
  html:
    toc: false
---
## This page takes a while to load -- be patient

::: {.callout-tip title="Tips for navigating"}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model and frame size combinations.
3. Click on Rider Height checkbox to view frames of a specific size. The 175 height is the most complete.
4. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-tip title="Tips for size boxes"}
1. Use the Small/Medium/Large box to see only a single size per model
2. Use the Rider Height boxes to see all model sizes that fit you
:::

::: {.callout-tip title="More notes!"}
More notes at the bottom!
:::


[Click here to see a version of this page that simultaneously highlights all frame sizes within a model](../qmd/gravel_scatter_model.qmd)

```{r setup-gravel-scatter, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```

```{r make-plots}
#| echo: false
#| eval: true

geobike_shared <- SharedData$new(geobike, key = ~model_size, group = "2dscatter")

p1 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "reach", y_col = "stack",
                  x_label = "Reach (mm)", y_label = "Stack (mm)",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p2 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_center", y_col = "rear_center",
                  x_label = "Front Center (horizontal) (mm)", y_label = "Rear Center (horizontal) (mm)",
                  x_info = "FC", y_info = "RC",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p3 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "top_tube_effective_length", y_col = "seat_tube_effective_length",
                  x_label = "Top Tube (effective) (mm)", y_label = "Seat Tube (effective) (mm)",
                  x_info = "ETTL", y_info = "ESTL",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p4 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "wheelbase", y_col = "bottom_bracket_drop",
                  x_label = "Wheelbase (mm)", y_label = "Bottom Bracket Drop (mm)",
                  x_info = "WB", y_info = "BB drop",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p5 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "seat_tube_angle", y_col = "head_tube_angle",
                  x_label = "Seat Tube Angle (°)", y_label = "Head Tube Angle (°)",
                  x_info = "STA", y_info = "HTA", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p6 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "chainstay_length",
                  y_col = "seat_tube_length",
                  x_label = "Chainstay Length (mm)",
                  y_label = "Seat Tube Length (mm)",
                  x_info = "CS", y_info = "STL",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p7 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "seat_tube_length", y_col = "top_tube_angle",
                  x_label = "Seat Tube Length (mm)", y_label = "Top Tube Angle (°)",
                  x_info = "STL", y_info = "TTA", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p8 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "trail", y_col = "trail_45",
                  x_label = "Trail (mm)", y_label = "Trail (45 mm tire) (mm)",
                  x_info = "Trail", y_info = "Trail-45", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p9 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_wheelbase", y_col = "stack_reach",
                  x_label = "Front Center/Wheelbase", y_label = "Stack/Reach",
                  x_info = "FC/WB", y_info = "Stack/Reach", digits = 2,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p10 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_wheelbase", y_col = "sta_hta",
                  x_label = "Front Center/Wheelbase", y_label = "STA/HTA",
                  x_info = "FC/WB", y_info = "STA/HTA", digits = 2,
                  g_col = "model_size",
                  same_xy_scale = FALSE)

```

```{r working-output}
#| eval: true
#| echo: false
#| out-height: "100%"
#| out-width: "100%"


# set up check boxes


 # med_box <- filter_checkbox("med", "Classification size", geobike_shared, ~frame_size_std_m, inline = FALSE)
  
  # --- 2) Height checkbox grid (one Crosstalk filter per height column) --------
  make_height_box <- function(h) {
    var_form <- as.formula(paste0("~h", h))
    crosstalk::filter_checkbox(
      id = paste0("height_", h),
      label = NULL,               # visible label = the height number
      sharedData = geobike_shared,
      var_form,                               # IMPORTANT: the column, not 'group'
      inline = TRUE
    )
  }
  height_ticks <- c(seq(150, 200, by = 1)) # adjust range/step as you like
  height_boxes <- lapply(height_ticks, make_height_box)
  height_ticks_in <- c(seq(59, 79, by = 0.5)) # adjust range/step as you like
  height_boxes_in <- lapply(height_ticks_in, make_height_box)
  

  f1 <- filter_checkbox("material", "Frame material", geobike_shared, ~material, inline = TRUE)
  f2 <- filter_checkbox("handlebar", "Handlebar", geobike_shared, ~handlebar, inline = TRUE)
  f3 <- filter_checkbox("axle", "Hub spacing", geobike_shared, ~axle_spacing, inline = TRUE)
  f4 <- filter_checkbox("udh", "UDH", geobike_shared, ~udh, inline = TRUE)
  f5 <- filter_checkbox("dropper", "Stealth dropper", geobike_shared, ~stealth_dropper, inline = TRUE)
  f6 <- filter_checkbox("fork", "Suspension correction (mm)", geobike_shared, ~fork_class, inline = TRUE)
  f7 <- filter_checkbox("sliding", "Sliding dropout (mm)", geobike_shared, ~dropout, inline = TRUE)
  f8 <- filter_slider("tire_700", "Max 700c tire width (mm)", geobike_shared, ~tire_width_max_700c, step = 1)
  f9 <- filter_slider("tire_650", "Max 650b tire width (in)", geobike_shared, ~tire_width_max_650b, step = 0.05)
  f10 <- filter_slider("max_chainring", "Max 1X chainring", geobike_shared, ~max_chainring_1x)
  f11 <- filter_slider("frameset", "Frameset ($)", geobike_shared, ~frameset_usd)
  f12 <- filter_slider("base_build", "Base Build ($)", geobike_shared, ~base_build_usd)
  f13 <- filter_checkbox("country", "Location", geobike_shared, ~country, inline = TRUE)

    
left_col <- tagList(p1, br(), p2, br(), p3, br(), p4, br(), p5, br(), p6, br(), p7, br(), p8, br(), p9, br(), p10)

# --- 5) Styling: two-column layout + sticky filter panel + pretty height grid -
styles <- tags$style(HTML("
  .page-grid {
    display: grid;
    grid-template-columns: minmax(400px, 1fr) 340px;  /* left flexible, right fixed */
    gap: 16px;
  }
  @media (max-width: 1100px) {
    .page-grid { grid-template-columns: 1fr; }
  }
  .filters-panel {
    position: sticky; top: 8px; align-self: start;
    max-height: calc(100vh - 16px); overflow: auto;
    padding: 12px; border: 1px solid #ddd; border-radius: 10px;
    background: #fafafa;
  }
  .filter-card {
    border: 1px solid #e5e7eb; border-radius: 8px; padding: 10px; margin-bottom: 10px;
    background: white;
  }
  .filter-card h4 {
    margin: 0 0 6px 0; font-size: 1rem; font-weight: 600;
  }

  /* Height checkbox grid */
  .height-grid {
    display: grid;
    grid-template-columns: repeat(auto-fill, minmax(58px, 1fr));
    gap: 6px 10px;
    align-items: center;
  }
  .height-grid .crosstalk-input-checkbox .checkbox { margin: 0; }
  .height-grid label { margin: 0; font-size: 0.95rem; }

  .height-toolbar { display: flex; gap: 8px; align-items: center; margin-bottom: 8px; }
  .height-toolbar .pill { font-size: 0.85rem; padding: 2px 8px; background: #eef2ff; border-radius: 999px; }
"))

# --- 6) JS: make the height checkboxes single-select + Clear + default 175 ----
height_select <- tags$select(
  id = "height-select",
  class = "height-select",
  lapply(height_ticks, function(h) tags$option(value = h, h))
)

compact_css <- tags$style(HTML("
  .height-select { width: 100%; font-size: 13px; padding: 4px 8px; }
  /* Hide the checkbox grid but keep space for an optional 'Show advanced' link */
  .height-grid.is-hidden { display: none !important; }
"))

# --- JS: tie the select to the hidden checkboxes (and preserve your Clear button)
wire_js <- tags$script(HTML("
  (function(){
    function clickIfChecked(el, shouldBeChecked){
      if (!!el.checked !== !!shouldBeChecked) el.click(); // use click() so Crosstalk updates
    }
    function setHeightFromSelect(val){
      const boxes = document.querySelectorAll('.height-grid input[type=checkbox]');
      boxes.forEach(function(b){
        const label = b.parentElement && b.parentElement.textContent.trim();
        clickIfChecked(b, label === val);
      });
    }
    document.addEventListener('change', function(e){
      if (e.target && e.target.matches('#height-select')) {
        setHeightFromSelect(e.target.value);
      }
    });
    document.addEventListener('click', function(e){
      if (e.target && e.target.matches('#height-clear')) {
        const boxes = document.querySelectorAll('.height-grid input[type=checkbox]');
        boxes.forEach(function(b){ if (b.checked) b.click(); });
        const sel = document.querySelector('#height-select');
        if (sel) sel.selectedIndex = -1;  // clear selection
      }
    });
    // Initialize select to 175 if that box is preselected
    document.addEventListener('DOMContentLoaded', function(){
      var chosen = document.querySelector('#height_175 input[type=checkbox]');
      var sel = document.querySelector('#height-select');
      if (sel && chosen && chosen.checked) {
        sel.value = '175';
      }
    });
  })();
"))

# Compact CSS (reuse your existing one if you already have it)
compact_height_css_in <- tags$style(HTML("
  .height-select { width: 100%; font-size: 13px; padding: 4px 8px; }
  .height-grid-in.is-hidden { display: none !important; }
"))

# JS wiring for the INCH select <-> hidden checkboxes
height_select_in_js <- tags$script(HTML("
  (function(){
    function clickIfNeeded(box, shouldBeChecked){
      if (!!box.checked !== !!shouldBeChecked) box.click(); // trigger Crosstalk updates
    }
    function setFromSelectIn(val){
      const boxes = document.querySelectorAll('.height-grid-in input[type=checkbox]');
      boxes.forEach(function(b){
        const label = b.parentElement && b.parentElement.textContent.trim();
        clickIfNeeded(b, label === val);
      });
    }
    // Select -> hidden checkboxes
    document.addEventListener('change', function(e){
      if (e.target && e.target.matches('#height-select-in')) {
        setFromSelectIn(e.target.value);
      }
    });
    // Clear button for inches
    document.addEventListener('click', function(e){
      if (e.target && e.target.matches('#height-clear-in')) {
        document.querySelectorAll('.height-grid-in input[type=checkbox]')
          .forEach(function(b){ if (b.checked) b.click(); });
        const sel = document.querySelector('#height-select-in');
        if (sel) sel.selectedIndex = -1;
      }
    });
    // Checkbox -> select (keeps the dropdown in sync if the box changes elsewhere)
    document.addEventListener('change', function(e){
      if (e.target && e.target.matches('.height-grid-in input[type=checkbox]')) {
        if (!e.target.checked) return;
        const label = e.target.parentElement && e.target.parentElement.textContent.trim();
        const sel = document.querySelector('#height-select-in');
        if (sel) sel.value = label;
      }
    });
  })();
"))

# --- Build the section
height_section <- div(
  class = "filter-card",
  h4("Rider height (cm)"),
  div(class = "height-toolbar",
#      strong("Choose height (cm):"),
      tags$button(id = "height-clear", "See All")
  ),
  compact_css, wire_js,
  height_select,
  div(class = "height-grid is-hidden", height_boxes)  # keep boxes hidden
)

# The INCH section (put this alongside your cm 'height_section')
height_section_in <- div(
  class = "filter-card",
  h4("Rider height (in)"),
  div(class = "height-toolbar",
#      strong("Choose height (in):"),
      tags$button(id = "height-clear-in", "See All")
  ),
  compact_height_css_in,
  height_select_in_js,
  # The compact select — preselect a default by adding selected="selected" on an <option>
  tags$select(
    id = "height-select-in",
    class = "height-select",
    lapply(height_ticks_in, function(x) tags$option(value = x, x))
  ),
  # Keep the crosstalk checkboxes in the DOM (hidden)
  div(class = "height-grid-in is-hidden", height_boxes_in)
)

# --- 7) Assemble RIGHT column (filters) --------------------------------------

specs_section <- div(
  class = "filter-card",
  h4("Frame specs"),
  f1, f2, f3, f4, f5, f6, f7
)

tires_drivetrain_section <- div(
  class = "filter-card",
  h4("Tires & drivetrain"),
  f8, f9, f10
)

price_location_section <- div(
  class = "filter-card",
  h4("Price & location"),
  f11, f12, f13
)

right_col <- div(
  class = "filters-panel",
  height_section,
  height_section_in,     # NEW: the INCH dropdown + hidden grid
  specs_section,
  tires_drivetrain_section,
  price_location_section
)

# --- 8) Final page ------------------------------------------------------------
browsable(
  tagList(
    styles,
    div(class = "page-grid",
        div(left_col),
        right_col
    )
  )
)  


```

```{r old-make-plots}
#| echo: false
#| eval: false

geobike_shared <- SharedData$new(geobike, key = ~model_size, group = "2dscatter")

p1 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "reach", y_col = "stack",
                  x_label = "Reach (mm)", y_label = "Stack (mm)",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p2 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_center", y_col = "rear_center",
                  x_label = "Front Center (horizontal) (mm)", y_label = "Rear Center (horizontal) (mm)",
                  x_info = "FC", y_info = "RC",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p3 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "top_tube_effective_length", y_col = "seat_tube_effective_length",
                  x_label = "Top Tube (effective) (mm)", y_label = "Seat Tube (effective) (mm)",
                  x_info = "ETTL", y_info = "ESTL",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p4 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "wheelbase", y_col = "bottom_bracket_drop",
                  x_label = "Wheelbase (mm)", y_label = "Bottom Bracket Drop (mm)",
                  x_info = "WB", y_info = "BB drop",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p5 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "seat_tube_angle", y_col = "head_tube_angle",
                  x_label = "Seat Tube Angle (°)", y_label = "Head Tube Angle (°)",
                  x_info = "STA", y_info = "HTA", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p6 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "chainstay_length",
                  y_col = "seat_tube_length",
                  x_label = "Chainstay Length (mm)",
                  y_label = "Seat Tube Length (mm)",
                  x_info = "CS", y_info = "STL",
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p6 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "seat_tube_length", y_col = "top_tube_angle",
                  x_label = "Seat Tube Length (mm)", y_label = "Top Tube Angle (°)",
                  x_info = "STL", y_info = "TTA", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p8 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "trail", y_col = "trail_45",
                  x_label = "Trail (mm)", y_label = "Trail (45 mm tire) (mm)",
                  x_info = "Trail", y_info = "Trail-45", digits = 1,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p9 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_wheelbase", y_col = "stack_reach",
                  x_label = "Front Center/Wheelbase", y_label = "Stack/Reach",
                  x_info = "FC/WB", y_info = "Stack/Reach", digits = 2,
                  g_col = "model_size",
                  same_xy_scale = FALSE)
p10 <- scatter_fig(shared_data = geobike_shared,
                  link_group = "2dscatter",
                  x_col = "front_wheelbase", y_col = "sta_hta",
                  x_label = "Front Center/Wheelbase", y_label = "STA/HTA",
                  x_info = "FC/WB", y_info = "STA/HTA", digits = 2,
                  g_col = "model_size",
                  same_xy_scale = FALSE)


```


```{r old-plot}
#| eval: false
#| echo: false
#| out-height: "100%"
#| out-width: "100%"

# set up check boxes

  # gg_legend_ly <- ggplotly(gg_legend, width = 6.5*96, height = 1*96)

  #boxes <- filter_checkbox("size", "Size", geobike_shared, ~Size, inline = FALSE)
  sm_box <- filter_checkbox("small", "Small", geobike_shared, ~frame_size_std_s, inline = FALSE)
  med_box <- filter_checkbox("med", "Medium", geobike_shared, ~frame_size_std_m, inline = FALSE)
  lg_box <- filter_checkbox("large", "Large", geobike_shared, ~frame_size_std_l, inline = FALSE)
  height_boxes <- filter_checkbox("rider_height", "Rider Height", geobike_shared, ~frame_size_std_fine, inline = FALSE)


  f1 <- filter_checkbox("material", "Frame material", geobike_shared, ~material, inline = TRUE)
  f2 <- filter_checkbox("handlebar", "Handlebar", geobike_shared, ~handlebar, inline = TRUE)
  f3 <- filter_checkbox("axle", "Hub spacing", geobike_shared, ~axle_spacing, inline = TRUE)
  f4 <- filter_checkbox("udh", "UDH", geobike_shared, ~udh, inline = TRUE)
  f5 <- filter_checkbox("dropper", "Stealth dropper", geobike_shared, ~stealth_dropper, inline = TRUE)
  f6 <- filter_checkbox("fork", "Suspension correction (mm)", geobike_shared, ~fork_class, inline = TRUE)
  f7 <- filter_checkbox("sliding", "Sliding dropout (mm)", geobike_shared, ~dropout, inline = TRUE)
  f8 <- filter_slider("tire_700", "Max 700c tire width (mm)", geobike_shared, ~tire_width_max_700c, step = 1)
  f9 <- filter_slider("tire_650", "Max 650b tire width (in)", geobike_shared, ~tire_width_max_650b, step = 0.05)
  f10 <- filter_slider("max_chainring", "Max 1X chainring", geobike_shared, ~max_chainring_1x)
  f11 <- filter_slider("frameset", "Frameset ($)", geobike_shared, ~frameset_usd)
  f12 <- filter_slider("base_build", "Base Build ($)", geobike_shared, ~base_build_usd)
  f13 <- filter_checkbox("country", "Location", geobike_shared, ~country, inline = TRUE)
    
  
  bscols(
  widths = c(8, 4),
  # LEFT: plots stacked
  tags$div(style="display:flex; flex-direction:column; gap:20px;", p1, p2, p3, p4,
           p5, p6, p7, p8, p9),

  # RIGHT: filters — top row has 2 side-by-side, then the rest stacked
  tagList(
    # row with two inline filters
    bscols(widths = c(6,6), list(sm_box, med_box, lg_box), height_boxes),
    # stacked filters
    tags$div(style="display:flex; flex-direction:column; gap:12px;",
      f1, f2, f3, f4, f5, f6, f7, f8, f9, f10, f11, f12, f13
    )
  )
)
  


```

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 175 cm high rider (generally frame size M or 54), according to manufacturer's charts.
:::

