---
title: "How does a suspension fork change bike geometry -- Tables of data"
---
::: {.callout-tip title="How to search for a specific model and size!"}
1. Use the pop-up box at the upper-left to search for a specific bike model and size.
2. If there is already a model in the pop-up box then
i. click in the box
ii. hit the delete key
iii. start typing model name.
:::

::: {.callout-tip}
More notes at the bottom!
:::


```{r gravel-sus-setup, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)

```


```{r geom-table, echo=FALSE, eval=TRUE}

row_i <- 573 # sklar ML
table_cols <- c("axle_crown", "stack", "reach", "head_tube_angle", "seat_tube_angle", "bottom_bracket_drop", "wheelbase", "front_center", "rear_center", "trail_45")
clean_cols <- c("fork length", "stack", "reach", "head tube angle", "seat tube angle", "BB drop", "wheelbase", "frontcenter", "rearcenter", "trail (45mm)")

geom_table <- data.table(NULL)

#for(row_i in 1:nrow(geobike)){
for(row_i in 1:nrow(geobike)){
  rigid <- geobike[row_i, .SD, .SDcols = table_cols] |> as.numeric()
  # rigid[1] <- round(rigid[1], 0) # make axle-crown an integer
  rudy_30_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "30 45")] |> as.numeric()
  rudy_30_51 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "30 51")] |> as.numeric()
  rudy_40_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "40 45")] |> as.numeric()
  rudy_40_51 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "40 51")] |> as.numeric()
  fox_50_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "50 45")] |> as.numeric()
  fox_50_50 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "50 50")] |> as.numeric()
  value_table <- data.table(
    rigid,
      rudy_30_45,
      rudy_40_45,
      rudy_30_51,
      rudy_40_51,
      fox_50_45,
      fox_50_50
  ) |>
    round(1)
  value_table <- apply(value_table, 2, as.character)
  for(i in c(1:3,6:10)){
    x <- value_table[i, ]
    x <- str_remove(x, "\\..*")
    value_table[i, ] <- x
  }
  colnames(value_table) <- c(
    "Rigid",
    "30 mm Travel, 45 mm Offset",
    "40 mm Travel, 45 mm Offset",
    "30 mm Travel, 51 mm Offset",
    "40 mm Travel, 51 mm Offset",
    "50 mm Travel, 45 mm Offset",
    "50 mm Travel, 50 mm Offset"
  )

  geom_table <- rbind(
    geom_table,
    data.table(
      Model = geobike[row_i, model_size],
      Measure = clean_cols,
#      Rigid = rigid,
      value_table
    ))
}

geom_table_shared <- SharedData$new(geom_table, group = "model_group")

fig <- datatable(geom_table_shared,
                 rownames = FALSE,
                 options = list(autoWidth = TRUE))


filter_ui <- filter_select(id = "fsid", 
                           label = "Model", 
                           sharedData = geom_table_shared, 
                           group = ~Model,
                           multiple = FALSE)


 p <- bscols(widths = c(2, 10), filter_ui, fig
  )
  
 p



```



::: {.callout-note}
The suspension fork length and geometry is based on 20% sag: fork_length - 0.2*travel
:::

::: {.callout-warning title="A Rudy Fork geometry corrector"}
Rockshox recommends 5% sag on the Rudy fork while Fox, Cane Creek, and Lauf recommend (or are tuned for) 20% sag. The sus geometry for a 30 mm Rudy fork will be about 1/2 way between the 30 mm and 40 mm measures (for the same offset). The sus geometry for a 40 mm Rudy fork will be about 3/5 way between the 40 mm and 50 mm measures (for the same offset).
:::

::: {.callout-warning title="Is your frame suspension corrected?"}
Several companies are calling their frame suspension corrected, or sell a suspension fork with a build, but their rigid Axle-Crown length is far short (by > 10 mm and often > 15 mm) the sagged length of a 30 mm fork.
:::

::: {.callout-tip title="Gravel forks"}
1. Cane Creek Invert has two models: 30 mm (425 mm axle-crown) and 40 (435 mm axle-crown) mm travel. Both models have 45 mm offset
2. Rockshox Rudy has four models: 30 mm (425 mm axle-crown) and 40 (435 mm axle-crown) mm travel, each with either 45 mm or 51 mm offset.
3. Fox 32 TC Factory has four models: 40 (435.5 mm axle-crown) mm and 50 (445.5 mm axle-crown) mm travel, each with either 45 mm or 50 mm offset.
4. Lauf has one model with 30 mm travel (425 Axle Crown and 47 mm offset)
:::

