---
title: "How does a suspension fork change bike geometry?"
subtitle: "And how race/rowdy/relaxed are they?"
---

```{r gravel-sus-setup, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)

```


```{r geom-table, echo=FALSE, eval=TRUE}
library(DT)
library(reactable)

row_i <- 573 # sklar ML
table_cols <- c("axle_crown", "stack", "reach", "head_tube_angle", "seat_tube_angle", "bottom_bracket_drop", "wheelbase", "front_center", "rear_center", "trail")
clean_cols <- c("fork length", "stack", "reach", "head tube angle", "seat tube angle", "BB drop", "wheelbase", "frontcenter", "rearcenter", "trail")

geom_table <- data.table(NULL)

#for(row_i in 1:nrow(geobike)){
for(row_i in 1:nrow(geobike)){
  rigid <- geobike[row_i, .SD, .SDcols = table_cols] |> as.numeric()
  rudy_30_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "30 45")] |> as.numeric()
  rudy_30_51 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "30 51")] |> as.numeric()
  rudy_40_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "40 45")] |> as.numeric()
  rudy_40_51 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "40 51")] |> as.numeric()
  fox_50_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "50 45")] |> as.numeric()
  fox_50_50 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "50 50")] |> as.numeric()
  value_table <- data.table(
      rudy_30_45,
      rudy_40_45,
      rudy_30_51,
      rudy_40_51,
      fox_50_45,
      fox_50_50
  ) |>
    round(1)
  value_table <- apply(value_table, 2, as.character)
  for(i in c(1:3,6:10)){
    x <- value_table[i, ]
    x <- str_remove(x, "\\..*")
    value_table[i, ] <- x
  }
  colnames(value_table) <- c(
    "30 mm Travel, 45 mm Offset",
    "40 mm Travel, 45 mm Offset",
    "30 mm Travel, 51 mm Offset",
    "40 mm Travel, 51 mm Offset",
    "50 mm Travel, 45 mm Offset",
    "50 mm Travel, 50 mm Offset"
  )

  geom_table <- rbind(
    geom_table,
    data.table(
      Model = geobike[row_i, model_size],
      Measure = clean_cols,
      Rigid = as.integer(rigid),
      value_table
    ))
}

geom_table_shared <- SharedData$new(geom_table, group = "model_group")

fig <- datatable(geom_table_shared,
                 options = list(autoWidth = TRUE,
                                rownames = FALSE))


filter_ui <- filter_select(id = "fsid", 
                         label = "Model", 
                         sharedData = geom_table_shared, 
                         group = ~Model,
                         multiple = FALSE)


 p <- bscols(widths = c(2, 10), filter_ui, fig
  )
  
  p



```





::: {.callout-tip title="How does a suspension change bike geometry?"}
1. Cane Creek Invert has two models: 30 mm (425 mm axle-crown) and 40 (435 mm axle-crown) mm travel. Both models have 45 mm offset
2. Rockshox Rudy has four models: 30 mm (425 mm axle-crown) and 40 (435 mm axle-crown) mm travel, each with either 45 mm or 51 mm offset.
3. Fox 32 TC Factory has four models: 40 (435.5 mm axle-crown) mm and 50 (445.5 mm axle-crown) mm travel, each with either 45 mm or 50 mm offset.
:::

::: {.callout-note}
1. The suspension fork length is based on 10% sag: fork_length - 0.1*travel
:::

