---
title: "How does a suspension fork change my bike geometry?"
editor: source
format:
  html:
    toc: false
---
::: {.callout-tip}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model and frame size combinations.
3. Click on **Focal** checkbox to view only the frame size used for the classification.
4. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 176 cm (5' 9.3") high rider, according to manufacturer's charts.
:::

[Click here to see a version of this page that simultaneously highlights all frame sizes within a model](../qmd/gravel_scatter_model.qmd)

```{r setup-gravel-scatter, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```



```{r plot-headers, warning=FALSE, message=FALSE, eval=FALSE, echo=FALSE, out.width = "90%", out.height = "90%"}

### Stack vs. Reach
### Chainstay Length vs. Effective top tube length
### Rear Center vs. Front Center
### Head Tube Angle vs. Seat Tube Angle
### Top Tube Angle vs. Seat Tube Angle
### Trail vs. Head Tube Angle
### Stack/Reach vs. Front Center/Wheelbase
### Seat Tube Angle/Head Tube Angle vs. Front Center/Wheelbase

```

```{r make-plots, echo=FALSE}
#geobike_sus_shared <- SharedData$new(geobike_sus[my_fit == TRUE,], key = ~model_size, group = "2dsus")
geobike_sus_shared <- SharedData$new(geobike_sus[my_fit == TRUE,], key = ~row_id, group = "2dsus")

p1 <- scatter_fig(shared_data = geobike_sus_shared,
                  link_group = "2dsus",
                  x_col = "reach", y_col = "stack",
                  x_label = "Reach (mm)", y_label = "Stack (mm)",
                  g_col = "model_size",
                  filter_col = "fork_key",
                  filter_keep = "rigid",
                  label_col = "label",
                  xtra_info = "fork",
                  same_xy_scale = FALSE)
p2 <- scatter_fig(shared_data = geobike_sus_shared,
                  link_group = "2dsus",
                  x_col = "seat_tube_angle", y_col = "head_tube_angle",
                  x_label = "Seat Tube Angle (°)", y_label = "Head Tube Angle (°)",
                  x_info = "STA", y_info = "HTA", digits = 1,
                  g_col = "model_size",
                  filter_col = "fork_key",
                  filter_keep = "rigid",
                  label_col = "label",
                  xtra_info = "fork",
                  same_xy_scale = FALSE)
p3 <- scatter_fig(shared_data = geobike_sus_shared,
                  link_group = "2dsus",
                  x_col = "bottom_bracket_drop", y_col = "trail_45",
                  x_label = "Bottom Bracket Drop (mm)", y_label = "Trail (45 mm tire) (mm)",
                  x_info = "BB drop", y_info = "Trail-45", digits = 1,
                  g_col = "model_size",
                  filter_col = "fork_key",
                  filter_keep = "rigid",
                  label_col = "label",
                  xtra_info = "fork",
                  same_xy_scale = FALSE)
p4 <- scatter_fig(shared_data = geobike_sus_shared,
                  link_group = "2dsus",
                  x_col = "front_center", y_col = "rear_center",
                  x_label = "Front Center (H) (mm)", y_label = "Rear Center (H) (mm)",
                  x_info = "FC", y_info = "RC", digits = 1,
                  g_col = "model_size",
                  filter_col = "fork_key",
                  filter_keep = "rigid",
                  label_col = "label",
                  xtra_info = "fork",
                  same_xy_scale = FALSE)




```


```{r, echo = FALSE, out.height="100%", out.width="100%"}
# set up check boxes

  # gg_legend_ly <- ggplotly(gg_legend, width = 6.5*96, height = 1*96)

  boxes <- filter_checkbox("fork", "Fork", geobike_sus_shared, ~travel, inline = FALSE)
  bscols(widths = c(8,3), p1, boxes)
  bscols( widths = c(8,3), p2)
  bscols( widths = c(8,3), p3)
  bscols( widths = c(8,3), p4)

  # p3
  # p4
  # p5
  # p6
  # p7
  # p8
  # p9

```



