---
title: "How does a suspension fork change bike geometry -- Tables of data"
---
::: {.callout-tip title="How to search for a specific model and size!"}
1. Use the pop-up box at the upper-left to search for a specific bike model and size.
2. If there is already a model in the pop-up box then
i. click in the box
ii. hit the delete key
iii. start typing model name.
:::

::: {.callout-tip}
More notes at the bottom!
:::


```{r hardtail-sus-setup, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)

```

```{r sus-one-bike-long, echo=FALSE}
sus_one_bike_long <- function(old_geo, new_ac, new_travel, new_rake, new_sag){
  new_geo <- copy(old_geo)
  sus_measures <- geometry_with_sus_fork(
    old_geo[1], new_ac, new_travel, new_rake, new_sag)
  new_geo[1, axle_crown := sus_measures["axle_crown_sag"]]
  new_geo[1, wheelbase := sus_measures["wheelbase"]]
  new_geo[1, stack := sus_measures["stack"]]
  new_geo[1, reach := sus_measures["reach"]]
  new_geo[1, top_tube_effective_length_est := sus_measures["ttel"]]
  new_geo[1, head_tube_angle := sus_measures["hta"]]
  new_geo[1, seat_tube_angle := sus_measures["sta"]]
  new_geo[1, bottom_bracket_drop := sus_measures["bb_drop"]]
  new_geo[1, rear_center := sus_measures["rc"]]
  new_geo[1, front_center := sus_measures["fc"]]
  new_geo[1, trail_45 := sus_measures["trail_45"]]
  
  return(new_geo)
}
```

```{r sus-all-bikes-long, echo=FALSE}
sus_all_bikes_long <- function(old_geo, new_ac, new_travel, new_rake, new_sag){
  new_geo <- copy(old_geo)
  for(row_i in 1:nrow(bike_dt)){
    sus_measures <- geometry_with_sus_fork(
      old_geo[row_i], new_ac, new_travel, new_rake, new_sag)
    new_geo[row_i, axle_crown := sus_measures["axle_crown_sag"]]
    new_geo[row_i, wheelbase := sus_measures["wheelbase"]]
    new_geo[row_i, stack := sus_measures["stack"]]
    new_geo[row_i, reach := sus_measures["reach"]]
    new_geo[row_i, top_tube_effective_length_est := sus_measures["ttel"]]
    new_geo[row_i, head_tube_angle := sus_measures["hta"]]
    new_geo[row_i, seat_tube_angle := sus_measures["sta"]]
    new_geo[row_i, bottom_bracket_drop := sus_measures["bb_drop"]]
    new_geo[row_i, rear_center := sus_measures["rc"]]
    new_geo[row_i, front_center := sus_measures["fc"]]
    new_geo[row_i, trail_45 := sus_measures["trail_45"]]
  }
  return(new_geo)
}
```

```{r sus-all-bikes-wide, echo=FALSE}
sus_all_bikes_wide <- function(bike_dt, new_ac, new_travel, new_rake, new_sag){
  for(row_i in 1:nrow(bike_dt)){
    sus_specs = paste(new_travel, new_rake, sep = "_")
    sus_measures <- geometry_with_sus_fork(
      bike_dt[row_i], new_ac, new_travel, new_rake, new_sag)
    bike_dt[row_i, (paste("axle_crown", sus_specs)) :=
           sus_measures["axle_crown_sag"]]
    bike_dt[row_i, (paste("wheelbase", sus_specs)) :=
           sus_measures["wheelbase"]]
    bike_dt[row_i, (paste("stack", sus_specs)) :=
           sus_measures["stack"]]
    bike_dt[row_i, (paste("reach", sus_specs)) :=
           sus_measures["reach"]]
    bike_dt[row_i, (paste("top_tube_effective_length_est", sus_specs)) :=
           sus_measures["ttel"]]
    bike_dt[row_i, (paste("head_tube_angle", sus_specs)) :=
           sus_measures["hta"]]
    bike_dt[row_i, (paste("seat_tube_angle", sus_specs)) :=
           sus_measures["sta"]]
    bike_dt[row_i, (paste("bottom_bracket_drop", sus_specs)) :=
           sus_measures["bb_drop"]]
    bike_dt[row_i, (paste("rear_center", sus_specs)) :=
           sus_measures["rc"]]
    bike_dt[row_i, (paste("front_center", sus_specs)) :=
           sus_measures["fc"]]
    bike_dt[row_i, (paste("trail_45", sus_specs)) :=
           sus_measures["trail_45"]]
  }
  
}
```

```{r hardtail-sus-data, echo=FALSE}

table_cols <- c("axle_crown", "stack", "reach", "top_tube_effective_length_est", "head_tube_angle", "seat_tube_angle", "bottom_bracket_drop", "wheelbase", "front_center", "rear_center", "trail_45")
keep_cols <- c("model_size", "fork", "suspension_corrected","axle_crown_est", "axle_crown_rigid", "fork_travel", "fork_offset_rake", "fork_sag", "fork_sag_est", "wheel_size", paste0("x", 1:7), paste0("y", 1:7), table_cols)
clean_cols <- c("sagged fork length", "stack", "reach", "head tube angle", "seat tube angle", "BB drop", "wheelbase", "front center (horiz)", "rearcenter (horiz)", "trail (45mm)")

hardtails <- geobike[axle_crown > 480, .SD, .SDcols = keep_cols]

# fill in data for bikes with rigid forks
    #geobike[my_fit == TRUE & fork == "rigid" & axle_crown > 480, .SD, .SDcols = c("model", "axle_crown", "fork_travel")]

# rigid axle crown
hardtails[fork == "rigid", axle_crown_rigid := axle_crown]

hardtails[, sag_working := ifelse(is.na(fork_sag), fork_sag_est, fork_sag)]

# unsag any sagged bike. This produces rigid spec suspension fork
sus_dt <- data.table(NULL)
for(i in 1:nrow(hardtails)){
  # i <- 141 # Fairlight Holt 2.0 2025 M
  old_geo <- hardtails[i]
  if(old_geo[, fork_travel] > 0 & old_geo[, sag_working] != 0){
    new_ac <- old_geo[, axle_crown_rigid]
    new_travel <- old_geo[, fork_travel]
    new_rake <- old_geo[, fork_offset_rake]
    new_sag <- 0
    new_geo <- sus_one_bike_long(old_geo, new_ac, new_travel, new_rake, new_sag)
  }else{
    new_geo <- copy(old_geo)
  }
  sus_dt <- rbind(sus_dt,new_geo)
}
fork_dt <- data.table(
  fork = "Rigid",
  sus_dt
)

# spec fork with 20% sag
sus_dt <- data.table(NULL)
for(i in 1:nrow(hardtails)){
  # i <- 141 # Fairlight Holt 2.0 2025 M
  old_geo <- hardtails[i]
  new_ac <- old_geo[, axle_crown_rigid]
  new_travel <- old_geo[, fork_travel]
  new_rake <- old_geo[, fork_offset_rake]
  new_sag <- 0.2
  new_geo <- sus_one_bike_long(old_geo, new_ac, new_travel, new_rake, new_sag)
  sus_dt <- rbind(sus_dt,new_geo)
}
fork_dt <- rbind(data.table(
  fork = "20%",
  sus_dt
)
)



```

```{r geom-table, echo=FALSE, eval=TRUE}

row_i <- 573 # sklar ML
table_cols <- c("axle_crown", "stack", "reach", "head_tube_angle", "seat_tube_angle", "bottom_bracket_drop", "wheelbase", "front_center", "rear_center", "trail_45")
clean_cols <- c("fork length", "stack", "reach", "head tube angle", "seat tube angle", "BB drop", "wheelbase", "frontcenter", "rearcenter", "trail (45mm)")

geom_table <- data.table(NULL)

#for(row_i in 1:nrow(geobike)){
for(row_i in 1:nrow(geobike)){
  rigid <- geobike[row_i, .SD, .SDcols = table_cols] |> as.numeric()
  # rigid[1] <- round(rigid[1], 0) # make axle-crown an integer
  rudy_30_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "30 45")] |> as.numeric()
  rudy_30_51 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "30 51")] |> as.numeric()
  rudy_40_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "40 45")] |> as.numeric()
  rudy_40_51 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "40 51")] |> as.numeric()
  fox_50_45 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "50 45")] |> as.numeric()
  fox_50_50 <- geobike[row_i, .SD, .SDcols = paste(table_cols, "50 50")] |> as.numeric()
  value_table <- data.table(
    rigid,
      rudy_30_45,
      rudy_30_51,
      rudy_40_45,
      rudy_40_51,
      fox_50_45,
      fox_50_50
  ) |>
    round(1)
  value_table <- apply(value_table, 2, as.character)
  for(i in c(1:3,6:10)){
    x <- value_table[i, ]
    x <- str_remove(x, "\\..*")
    value_table[i, ] <- x
  }
  colnames(value_table) <- c(
    "Rigid",
    "30 mm Travel, 45 mm Offset",
    "30 mm Travel, 51 mm Offset",
    "40 mm Travel, 45 mm Offset",
    "40 mm Travel, 51 mm Offset",
    "50 mm Travel, 45 mm Offset",
    "50 mm Travel, 50 mm Offset"
  )
  
  geom_table <- rbind(
    geom_table,
    data.table(
      Model = geobike[row_i, model_size],
      Measure = clean_cols,
#      Rigid = rigid,
      value_table
    ))
}

# 1) a soft highlight color for the hovered column (body + header)
hover_css <- tags$style(HTML("
  table.dataTable tbody td.col-hover,
  table.dataTable thead th.col-hover {
    background-color: #fff3cd !important; /* pale amber */
  }
"))

# 2) JS to add/remove the .col-hover class based on the cell under the cursor
hover_js <- JS("
  table.on('mouseenter', 'td', function() {
    var idx = table.cell(this).index().column;
    // clear any previous highlights
    $(table.cells().nodes()).removeClass('col-hover');
    $(table.columns().header()).removeClass('col-hover');
    // add to this column (body + header)
    $(table.column(idx).nodes()).addClass('col-hover');
    $(table.column(idx).header()).addClass('col-hover');
  });
  table.on('mouseleave', function() {
    // remove when pointer leaves the table
    $(table.cells().nodes()).removeClass('col-hover');
    $(table.columns().header()).removeClass('col-hover');
  });
")

# --- 1) Column-hover style (header + body) ---
col_css <- tags$style(HTML("
  table.dataTable thead th.col-hover,
  table.dataTable tbody td.col-hover {
    background-color: rgba(255, 243, 205, 0.85) !important; /* pale amber */
  }
"))

# --- 2) JS: highlight column on hover (body *and* header) ---
col_js <- JS("
  function clearHighlights() {
    $(table.cells().nodes()).removeClass('col-hover');
    $(table.columns().header()).removeClass('col-hover');
    var fh = $('.fixedHeader-floating thead th');
    if (fh.length) fh.removeClass('col-hover');
  }

  // BODY: hover over a data cell -> highlight its column
  table.on('mouseenter', 'tbody td', function() {
    var c = table.cell(this).index().column;  // DataTables column index
    clearHighlights();
    $(table.column(c).nodes()).addClass('col-hover');     // body
    $(table.column(c).header()).addClass('col-hover');    // header
    var fh = $('.fixedHeader-floating thead th');         // FixedHeader support
    if (fh.length) fh.eq(table.column(c).index()).addClass('col-hover');
  });

  // HEADER: hover over a header cell -> highlight its column
  table.on('mouseenter', 'thead th', function() {
    // Use visible-index to handle ColReorder; map to the column
    var visibleIdx = $(this).index();
    var col = table.column(visibleIdx + ':visible');  // select that visible column
    clearHighlights();
    $(col.nodes()).addClass('col-hover');             // body
    $(col.header()).addClass('col-hover');            // header
    var fh = $('.fixedHeader-floating thead th');     // FixedHeader support
    if (fh.length) fh.eq(visibleIdx).addClass('col-hover');
  });

  // When pointer leaves the table area, clear
  table.on('mouseleave', function() { clearHighlights(); });
  table.on('mouseleave', 'thead', function() { clearHighlights(); });
")

# --- 1) Styles: column + row only (no intersection styling) ---
rc_hover_css <- tags$style(HTML("
  /* column (body + header) */
  table.dataTable tbody td.col-hover,
  table.dataTable thead th.col-hover {
    background-color: rgba(255, 243, 205, 0.85) !important; /* pale amber */
  }
  /* row (entire row across columns) */
  table.dataTable tbody tr.row-hover > td {
    background-color: rgba(205, 235, 255, 0.35) !important; /* pale blue */
  }
"))

# --- 2) JS: add/remove only row + column classes (no cell-focus) ---
rc_hover_js <- JS("
  table.on('mouseenter', 'tbody td', function() {
    var cell = table.cell(this);
    var idx  = cell.index();
    var r = idx.row, c = idx.column;

    // clear previous
    $(table.cells().nodes()).removeClass('col-hover');
    $(table.rows().nodes()).removeClass('row-hover');
    $(table.columns().header()).removeClass('col-hover');

    // add row highlight
    $(table.row(r).nodes()).addClass('row-hover');

    // add column highlight (body + header)
    $(table.column(c).nodes()).addClass('col-hover');
    $(table.column(c).header()).addClass('col-hover');
  });

  table.on('mouseleave', function() {
    $(table.cells().nodes()).removeClass('col-hover');
    $(table.rows().nodes()).removeClass('row-hover');
    $(table.columns().header()).removeClass('col-hover');
  });
")

first_bike <- geom_table$model_size[1] # pick the first bike name

geom_table_shared <- SharedData$new(geom_table, group = "model_group")

fig <- datatable(geom_table_shared,
                 rownames = FALSE,
                 options = list(
                   autoWidth = TRUE,
                   columnDefs = list(
                     list(visible = FALSE, targets = c(0))
                   )
                 ),
                 callback = col_js
) |> htmlwidgets::prependContent(col_css)


filter_ui <- filter_select(id = "fsid", 
                           label = "Model", 
                           sharedData = geom_table_shared, 
                           group = ~Model,
                           multiple = FALSE
)

 p <- bscols(widths = c(2, 10), filter_ui, fig
  )
  
 p



```

```{js echo=FALSE}
function filter_default() {
    document.getElementById("Model").getElementsByClassName("selectized") 
[0].selectize.setValue("3T Extrema Italia 2025", false);
 }
window.onload = filter_default;
```

::: {.callout-note}
The suspension fork length and geometry is based on 20% sag: fork_length - 0.2*travel
:::

::: {.callout-warning title="A Rudy Fork geometry corrector"}
Rockshox recommends 5% sag on the Rudy fork while Fox, Cane Creek, and Lauf recommend (or are tuned for) 20% sag. The sus geometry for a 30 mm Rudy fork will be about 1/2 way between the 30 mm and 40 mm measures (for the same offset). The sus geometry for a 40 mm Rudy fork will be about 3/5 way between the 40 mm and 50 mm measures (for the same offset).
:::

::: {.callout-warning title="Is your frame suspension corrected?"}
Several companies are calling their frame suspension corrected, or sell a suspension fork with a build, but their rigid Axle-Crown length is far short (by > 10 mm and often > 15 mm) the sagged length of a 30 mm fork.
:::

::: {.callout-tip title="Gravel forks"}
1. Cane Creek Invert has two models: 30 mm (425 mm axle-crown) and 40 (435 mm axle-crown) mm travel. Both models have 45 mm offset
2. Rockshox Rudy has four models: 30 mm (425 mm axle-crown) and 40 (435 mm axle-crown) mm travel, each with either 45 mm or 51 mm offset.
3. Fox 32 TC Factory has four models: 40 (435.5 mm axle-crown) mm and 50 (445.5 mm axle-crown) mm travel, each with either 45 mm or 50 mm offset.
4. Lauf has one model with 30 mm travel (425 Axle Crown and 47 mm offset)
:::

