---
title: "Is a gravel bike a 1990s mountain bike?"
---

```{r setup-mtb90s, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("Rmd", "bike_geometry_project.R")
source(source_path)

```

```{r import, echo=FALSE, warning=FALSE, message=FALSE }
import_it <- TRUE
if(import_it != TRUE){
  mtb90s_bike_path <- here("rds", "geobike.Rds")
  mtb90s <- readRDS(mtb90s_bike_path)
}else{
  data_path <- here(data_folder, "1990s mtn bikes_list.txt")
  bike_list <- fread(data_path)
  mtb90s <- data.table(NULL)
  for(i in 1:nrow(bike_list)){
    bike_label_i <- as.character(bike_list[i, "model"])
    bike_range_i <- as.character(bike_list[i, "data_range"])
    bike_i <- read_bike(bike_label = bike_label_i,
                        bike_range = bike_range_i,
                        data_file = "1990s mtn bikes.xlsx")
    bike_i[, my_fit := ifelse(frame_size == c(bike_list[i, "my_fit"]), TRUE, FALSE)]
    mtb90s <- rbind(mtb90s, bike_i)
  }

new_level <- "mid 90s MTB"
mtb90s[, restyle := new_level]

#combine with my_fit using subset of columns
  mtb_cols <- c("model", "year", "frame_size", "reach", "stack", "rear_center", "front_center", "head_tube_angle", "seat_tube_angle", "bottom_bracket_drop", "trail", "front_wheelbase", "stack_reach", "sta_hta", "restyle")
  
gravel_mtb90s <- rbind(my_fit[, .SD, .SDcols = mtb_cols],
                       mtb90s[my_fit == TRUE, .SD, .SDcols = mtb_cols])
restyle_levels <- c(levels(my_fit[, restyle]), new_level)
gravel_mtb90s[, restyle := factor(restyle,
              levels = restyle_levels)]
  
  
  
}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
annotate_model_i <- mtb90s[my_fit == TRUE, model]
plotted_data <- gravel_mtb90s
p1 <- scatter_fig(x_col = "reach", y_col = "stack",
                  x_label = "Reach", y_label = "Stack",
                  data = plotted_data,
                  annotate_model = annotate_model_i)
p2 <- scatter_fig(x_col = "rear_center", y_col = "front_center",
                  x_label = "Rear Center", y_label = "Front Center",
                  x_info = "RC", y_info = "FC",
                  data = plotted_data,
                  annotate_model = annotate_model_i)
p3 <- scatter_fig(x_col = "head_tube_angle", y_col = "seat_tube_angle",
                  x_label = "Head Tube Angle", y_label = "Seat Tube Angle",
                  x_info = "HTA", y_info = "STA", digits = 1,
                  jitter_x = 0,
                  jitter_y = 0,
                  data = plotted_data,
                  annotate_model = annotate_model_i)
p4 <- scatter_fig(x_col = "trail", y_col = "bottom_bracket_drop",
                  x_label = "Trail", y_label = "Bottom Bracket Drop",
                  x_info = "Trail", y_info = "BBD", digits = 0,
                  data = plotted_data,
                  annotate_model = annotate_model_i)
p5 <- scatter_fig(x_col = "front_wheelbase", y_col = "stack_reach",
                  x_label = "Front Center/Wheelbase", y_label = "Stack/Reach",
                  x_info = "FC/WB", y_info = "Stack/Reach", digits = 2,
                  data = plotted_data,
                  annotate_model = annotate_model_i)
p6 <- scatter_fig(x_col = "front_wheelbase", y_col = "sta_hta",
                  x_label = "Front Center/Wheelbase", y_label = "STA/HTA",
                  x_info = "FC/WB", y_info = "STA/HTA", digits = 2,
                  data = plotted_data,
                  annotate_model = annotate_model_i)
```


## No! 1990s mountain bikes have crazy low stack! {.unnumbered .unlisted}

```{r, echo=FALSE, warning=FALSE, message=FALSE}
p1
```


## No! 1990s mountain bikes have shorter rearends than Endurance gravel, shorter frontends than Trail gravel, and longer frontends than All-Road gravel! {.unnumbered .unlisted}

```{r, echo=FALSE, warning=FALSE, message=FALSE}
p2
```

## No! 1990s mountain bikes had upright head tube angles compared to Endurance and Trail gravel! {.unnumbered .unlisted}

```{r, echo=FALSE, warning=FALSE, message=FALSE}
p3
```

## No! 1990s mountain bikes have crazy small bottom bracket drops! {.unnumbered .unlisted}

```{r, echo=FALSE, warning=FALSE, message=FALSE}
p4
```

## No! 1990s mountain bikes have crazy low stack:reach! {.unnumbered .unlisted}

```{r, echo=FALSE, warning=FALSE, message=FALSE}
p5
```

## No! 1990s mountain bikes have low STA:HTA compared to Trail gravel and low STA:HTA given their relative front center compared to Endurance gravel {.unnumbered .unlisted}

```{r, echo=FALSE, warning=FALSE, message=FALSE}
p6
```
