---
title: "What makes a rowdy frame rowdy?"
editor: source
format:
  html:
    toc: false
---
::: {.callout-tip}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model and frame size combinations.
3. Click on **Focal** checkbox to view only the frame size used for the classification.
4. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 176 cm (5' 9.3") high rider, according to manufacturer's charts.
:::

```{r setup-gravel-scatter, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```

```{r legend, echo=FALSE, fig.width= 8, fig.height=0.5, eval=FALSE}
# plot_ly(data = geobike, type = "scatter", mode = "markers",
#         x = ~ reach,
#         y = ~ stack,
#         color = ~restyle,
#         colors = my_palette,
#         size = 10,
#         visible = "legendonly"
# )
#| fig-height: 1
gg <- ggplot(data = geobike,
       aes(x = reach,
           y = stack,
           color = restyle)) +
  geom_point() +
  scale_color_manual(name = "Classification",
                     values = pal_okabe_ito_3) +
  theme_pubr() +
  theme(legend.position="top") +
  NULL
  
gg_legend <- get_legend(gg)
plot_grid(gg_legend)

```

```{r plot-headers, warning=FALSE, message=FALSE, eval=FALSE, echo=FALSE, out.width = "90%", out.height = "90%"}

### Stack vs. Reach
### Chainstay Length vs. Effective top tube length
### Rear Center vs. Front Center
### Head Tube Angle vs. Seat Tube Angle
### Top Tube Angle vs. Seat Tube Angle
### Trail vs. Head Tube Angle
### Stack/Reach vs. Front Center/Wheelbase
### Seat Tube Angle/Head Tube Angle vs. Front Center/Wheelbase

```

```{r make-plots, echo=FALSE}

geobike_shared <- SharedData$new(my_fit)
add_regression <- TRUE

p1 <- scatter_fig_global(data = geobike_shared,
                  y_col = "rowdy", x_col = "stack",
                  y_label = "Rowdy Index", x_label = "Stack (mm)",
                  g_col = "model_size",
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p2 <- scatter_fig_global(data = geobike_shared,
                  y_col = "rowdy", x_col = "reach",
                  y_label = "Rowdy Index", x_label = "Reach (mm)",
                  g_col = "model_size",
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p3 <- scatter_fig_global(data = geobike_shared,
                  y_col = "rowdy", x_col = "head_tube_angle",
                  y_label = "Rowdy Index", x_label = "Head Tube Angle (°)",
                  g_col = "model_size",
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p4 <- scatter_fig_global(data = geobike_shared,
                  y_col = "rowdy", x_col = "seat_tube_angle",
                  y_label = "Rowdy Index", x_label = "Seat Tube Angle (°)",
                  g_col = "model_size",
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p5 <- scatter_fig_global(data = geobike_shared,
                  y_col = "rowdy", x_col = "fork_offset_rake",
                  y_label = "Rowdy Index", x_label = "Fork Offset (mm)",
                  g_col = "model_size",
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p6 <- scatter_fig_global(data = geobike_shared,
                  y_col = "rowdy", x_col = "chainstay_length",
                  y_label = "Rowdy Index", x_label = "Chainstay Length (mm)",
                  g_col = "model_size",
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p7 <- scatter_fig_global(data = geobike_shared,
                  y_col = "rowdy", x_col = "front_center",
                  y_label = "Rowdy Index", x_label = "Front Center (mm)",
                  g_col = "model_size",
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p8 <- scatter_fig_global(data = geobike_shared,
                  y_col = "rowdy", x_col = "stack_reach",
                  y_label = "Rowdy Index", x_label = "Stack:Reach",
                  g_col = "model_size",
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p9 <- scatter_fig_global(data = geobike_shared,
                  y_col = "rowdy", x_col = "front_rear",
                  y_label = "Rowdy Index", x_label = "Front Center:Rear Center",
                  g_col = "model_size",
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p10 <- scatter_fig_global(data = geobike_shared,
                  y_col = "rowdy", x_col = "trail",
                  y_label = "Rowdy Index", x_label = "Trail (mm)",
                  g_col = "model_size",
                  same_xy_scale = FALSE,
                  add_regression = add_regression)


# plot check boxes and fig
  # p <- bscols(
  #   widths = c(12), boxes
  # )
  # 
  # 

 #p
```


```{r check-boxes, echo = FALSE, out.height="100%", out.width="100%", eval=FALSE}
# set up check boxes
# this also plots p1

  # gg_legend_ly <- ggplotly(gg_legend, width = 6.5*96, height = 1*96)

  boxes <- filter_checkbox("size", "Size", geobike_shared, ~Size, inline = FALSE)
  # boxes$attribs$style <- css(font.size = "90%") # <-change the font size

  p <- bscols(
    widths = c(7,3,2), p1, boxes
  )
  p

  p <- bscols(
    widths = c(7,3,2), p2, boxes
  )
  p
  
# cowplot::plot_grid(gg_legend, boxes)
```


```{r plots, echo=FALSE, message=FALSE, warning=FALSE, out.height="100%", out.width="100%"}
# boxes
p1
p2
p3
p4
p5
p6
p7
p8
p9
#p10

```


