---
title: "What makes a racy frame racy?"
editor: source
format:
  html:
    toc: false
---
::: {.callout-tip}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model and frame size combinations.
3. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 175 cm high rider (generally frame size M or 54), according to manufacturer's charts.
:::


```{r setup-gravel-scatter, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```


```{r make-plots, echo=FALSE}

geobike_shared <- SharedData$new(my_fit)
add_regression <- TRUE

# p0 <- base_ternary(data = geobike_shared,
#                    axis_cols = c("stack", "reach", "chainstay_length"),
#                    axis_labels = c("Stack", "Reach", "Chainstay"),
#                    g_col = "restyle"
#                    )

# which classifier
tree_class <- 1
functional_class <- 2
kmeans_class <- 3
mclust_class <- 4
racy_col <- c("tree_racy", "functional_racy", "kmeans_racy", "mclust_racy")[kmeans_class]
color_col <- c("tree_style", "functional_style", "kmeans_style", "mclust_style")[kmeans_class]

p1 <- scatter_fig_global(data = geobike_shared,
                  y_col = racy_col, x_col = "stack",
                  y_label = "Racy Index", x_label = "Stack (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p2 <- scatter_fig_global(data = geobike_shared,
                  y_col = racy_col, x_col = "reach",
                  y_label = "Racy Index", x_label = "Reach (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p3 <- scatter_fig_global(data = geobike_shared,
                  y_col = racy_col, x_col = "head_tube_angle",
                  y_label = "Racy Index", x_label = "Head Tube Angle (°)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p4 <- scatter_fig_global(data = geobike_shared,
                  y_col = racy_col, x_col = "seat_tube_angle",
                  y_label = "Racy Index", x_label = "Seat Tube Angle (°)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p5 <- scatter_fig_global(data = geobike_shared,
                  y_col = racy_col, x_col = "bottom_bracket_drop",
                  y_label = "Racy Index", x_label = "Bottom Bracket Drop (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p6 <- scatter_fig_global(data = geobike_shared,
                  y_col = racy_col, x_col = "chainstay_length",
                  y_label = "Racy Index", x_label = "Chainstay Length (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p7 <- scatter_fig_global(data = geobike_shared,
                  y_col = racy_col, x_col = "front_center",
                  y_label = "Racy Index", x_label = "Front Center (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p8 <- scatter_fig_global(data = geobike_shared,
                  y_col = racy_col, x_col = "stack_reach",
                  y_label = "Racy Index", x_label = "Stack:Reach",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p9 <- scatter_fig_global(data = geobike_shared,
                  y_col = racy_col, x_col = "front_rear",
                  y_label = "Racy Index", x_label = "Front Center:Rear Center",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p10 <- scatter_fig_global(data = geobike_shared,
                  y_col = racy_col, x_col = "trail_45",
                  y_label = "Racy Index", x_label = "Trail (45 mm tire) (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)

```

### Racy bike frames have a combination of low stack, short front-center, high head tube angles, and low trail

```{r, echo = FALSE, message=FALSE, warning=FALSE, out.height="100%", out.width="100%"}
p1
p3
p7
p10
```

### Racy frames have short reach, relative to rowdy frames

```{r, echo = FALSE, message=FALSE, warning=FALSE, out.height="100%", out.width="100%"}

p2
```

### Racy frames have short chainstays (and rear-center), relative to relaxed frames

```{r, echo = FALSE, message=FALSE, warning=FALSE, out.height="100%", out.width="100%"}

p6
```

### Racy frames can have low seat tube angles

```{r, echo = FALSE, message=FALSE, warning=FALSE, out.height="100%", out.width="100%"}

p4
```

### Racy frames tend to have short front and rear centers. Relaxed frames tend to have long front and rear centers. So both racy and relaxed frames have low front-center:rear-center but for different reasons.

```{r}
p9

```

### Stack:Reach and bottom brack drop aren't really related to relaxedness

```{r, echo = FALSE, message=FALSE, warning=FALSE, out.height="100%", out.width="100%"}
p5
p8
```

