---
title: "What is Gravel Style?"
subtitle: "Gravel bike frame geometry can be Racy, Relaxed, or Rowdy"
---
It's common to read from company websites or from bike influencers on YouTube that gravel bikes come in two flavors: race and off-road. 2D scatter plots suggest three classes:

1. **Racy**. Effectively, these have cyclocross bike geometry
2. **Relaxed**. Compared to Racy: More upright, longer rearends, and longer trail -- this is the direction of endurance road bikes compared to race road bikes.
3. **Rowdy**. Compared to Racy: Longer, slacker front ends, and steeper seat tubes -- this is the direction of XC mountain bikes compared to road bikes.

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 176 cm (5' 9.3") cm high rider, according to manufacturer's charts.
:::

```{r what-is-gravel-bike-style-setup, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)

```


```{r what-is-gravel-bike-style-import, echo=FALSE, warning=FALSE, message=FALSE }
bikes_cols <- c("model", "year", "frame_size", "reach", "stack", "rear_center", "front_center", "head_tube_angle", "seat_tube_angle", "bottom_bracket_drop", "seat_tube_length", "top_tube_angle","trail", "front_wheelbase", "stack_reach", "sta_hta", "restyle", "model_size")
bikes <- my_fit[, .SD, .SDcols = bikes_cols]
opacity <- rep(0.5, nrow(bikes))

# import non-gravel bikes
# race
race <- import_bikes(style = "race", prefix = "Road: ")
bikes <- rbind(bikes,
               race[my_fit == TRUE, .SD, .SDcols = bikes_cols])
opacity <- c(opacity, rep(1.0, nrow(race[my_fit == TRUE,])))
# endurance
endurance <- import_bikes(style = "endurance", prefix = "Road: ")
bikes <- rbind(bikes,
               endurance[my_fit == TRUE, .SD, .SDcols = bikes_cols])
opacity <- c(opacity, rep(1.0, nrow(endurance[my_fit == TRUE,])))
# cross
cross <- import_bikes(style = "cyclocross", prefix = "Road: ")
bikes <- rbind(bikes,
               cross[my_fit == TRUE, .SD, .SDcols = bikes_cols])
opacity <- c(opacity, rep(1.0, nrow(cross[my_fit == TRUE,])))
# mountain
xc <- import_bikes(style = "mountain")
bikes <- rbind(bikes,
               xc[my_fit == TRUE, .SD, .SDcols = bikes_cols])
opacity <- c(opacity, rep(1.0, nrow(xc[my_fit == TRUE,])))

bikes[, brand := tstrsplit(model," ", keep = 1)]

```



```{r what-is-gravel-bike-style-plot, echo=FALSE, warning=FALSE, message=FALSE, out.width = "100%", out.height = "100%"}
p1 <- scatter_fig(data = bikes,
                  x_col = "reach", y_col = "stack",
                  g_col = "restyle",
                  x_label = "Reach (mm)", y_label = "Stack (mm)",
                  dot_opacity = opacity)
p2 <- scatter_fig(data = bikes,
                  x_col = "rear_center", y_col = "front_center",
                  g_col = "restyle",
                  x_label = "Rear Center (mm)", y_label = "Front Center (mm)",
                  x_info = "RC", y_info = "FC",
                  dot_opacity = opacity)
p3 <- scatter_fig(data = bikes,
                  x_col = "head_tube_angle", y_col = "seat_tube_angle",
                  g_col = "restyle",
                  x_label = "Head Tube Angle (째)", y_label = "Seat Tube Angle (째)",
                  x_info = "HTA", y_info = "STA", digits = 1,
                  dot_opacity = opacity)
p4 <- scatter_fig(data = bikes,
                  x_col = "seat_tube_length", y_col = "top_tube_angle",
                  g_col = "restyle",
                  x_label = "Seat Tube Length (mm)", y_label = "Top Tube Angle (째)",
                  x_info = "STL", y_info = "TTA", digits = 1,
                  dot_opacity = opacity,
                  same_xy_scale = FALSE)
p5 <- scatter_fig(data = bikes,
                  x_col = "head_tube_angle", y_col = "trail",
                  g_col = "restyle",
                  x_label = "Head Tube Angle (째)", y_label = "Trail (mm)",
                  x_info = "HTA", y_info = "Trail", digits = 1,
                  dot_opacity = opacity,
                  same_xy_scale = FALSE)
p6 <- scatter_fig(data = bikes,
                  x_col = "front_wheelbase", y_col = "stack_reach",
                  g_col = "restyle",
                  x_label = "Front Center/Wheelbase", y_label = "Stack/Reach",
                  x_info = "FC/WB", y_info = "Stack/Reach", digits = 2,
                  dot_opacity = opacity,
                  same_xy_scale = FALSE)
p7 <- scatter_fig(data = bikes,
                  x_col = "front_wheelbase", y_col = "sta_hta",
                  g_col = "restyle",
                  x_label = "Front Center/Wheelbase", y_label = "STA/HTA",
                  x_info = "FC/WB", y_info = "STA/HTA", digits = 2,
                  dot_opacity = opacity,
                  same_xy_scale = FALSE)
p1
p2
p3
p4
p5
p6
p7
```

