---
title: "What makes a relaxed frame relaxed?"
editor: source
format:
  html:
    toc: false
---
::: {.callout-tip}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model and frame size combinations.
3. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 175 cm high rider (generally frame size M or 54), according to manufacturer's charts.
:::


```{r setup-gravel-scatter, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```

```{r echo=FALSE, eval=FALSE}
cor(geobike[my_fit==TRUE &
              (kmeans_style == "relaxed" |
                 kmeans_style == "rowdy"), .SD, .SDcols=c("mds2", "stack_reach", "front_rear", "chainstay_length", "stack", "reach", "seat_tube_angle", "trail_45", "head_tube_angle")])
```


```{r make-plots, echo=FALSE}

relaxed_shared <- SharedData$new(geobike[my_fit == TRUE &
                                           (kmeans_style == "relaxed" | kmeans_style == "rowdy")],
                                 key = ~model_size, group = "2drelaxed")
add_regression <- TRUE

# which classifier
tree_class <- 1
functional_class <- 2
kmeans_class <- 3
mclust_class <- 4
relaxed_col <- c("tree_relaxed", "functional_relaxed", "kmeans_relaxed", "mclust_relaxed")[kmeans_class]
color_col <- c("tree_style", "functional_style", "kmeans_style", "mclust_style")[kmeans_class]
relaxed_col <- "mds2"

p1 <- scatter_fig(shared_data = relaxed_shared,
                  link_group = "2drelaxed",
                  y_col = relaxed_col, x_col = "chainstay_length",
                  y_label = "Relaxed Index", x_label = "Chainstay Length (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p2 <- scatter_fig(shared_data = relaxed_shared,
                  link_group = "2drelaxed",
                  y_col = relaxed_col, x_col = "stack",
                  y_label = "Relaxed Index", x_label = "Stack (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p3 <- scatter_fig(shared_data = relaxed_shared,
                  link_group = "2drelaxed",
                  y_col = relaxed_col, x_col = "seat_tube_angle",
                  y_label = "Relaxed Index", x_label = "Seat Tube Angle (°)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p4 <- scatter_fig(shared_data = relaxed_shared,
                  link_group = "2drelaxed",
                  y_col = relaxed_col, x_col = "reach",
                  y_label = "Relaxed Index", x_label = "Reach (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p5 <- scatter_fig(shared_data = relaxed_shared,
                  link_group = "2drelaxed",
                  y_col = relaxed_col, x_col = "head_tube_angle",
                  y_label = "Relaxed Index", x_label = "Head Tube Angle (°)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p6 <- scatter_fig(shared_data = relaxed_shared,
                  link_group = "2drelaxed",
                  y_col = relaxed_col, x_col = "trail_45",
                  y_label = "Relaxed Index", x_label = "Trail with 45 mm tire (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)


```



### Relaxed bike frames have a combination of long chain stays, high frame stack, and shallow seat tube angles

```{r relaxed-high, echo = FALSE, message=FALSE, warning=FALSE, out.height="100%", out.width="70%"}
# boxes
p1
p2
p3
```

### Reach, headtube angle, and trail aren't really related to relaxedness

```{r relaxed-low, echo = FALSE, message=FALSE, warning=FALSE, out.height="100%", out.width="70%"}
p4
p5
p6
```

