---
title: "GravelRrr"
subtitle: "Not just another bike geometry comparison tool"
---

```{r setup-index, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```

The [Gravel 2D](qmd/gravel_scatter.qmd) page contains interactive, 2D scatter plots of different pairs of frame geometry measures for all gravel bike models and frame sizes in the database.

```{r echo=FALSE}
image_folder <- "images"
image_file <- "gravel-scatter.png"
image_path <- here(image_folder, image_file)
include_graphics(image_path)
```

The [Gravel Ternary](qmd/gravel_ternary.qmd) page contains an interactive, ternary plot for all gravel bike models in the database. Each ternary plot axis is a style score (0 -- 100) for one of the styles: Racy, Relaxed, and Rowdy.

```{r echo=FALSE}
image_folder <- "images"
image_file <- "gravel-ternary.png"
image_path <- here(image_folder, image_file)
include_graphics(image_path)
```

The [What is Gravel Style?](qmd/what_is_a_gravel_bike.qmd) page contains interactive, 2D scatter plots of different pairs of frame geometry measures to compare gravel bikes in the database to Road Race, Road Endurance, Cyclocross, and XC Mountain bikes.

```{r echo=FALSE}
image_folder <- "images"
image_file <- "gravel-style.png"
image_path <- here(image_folder, image_file)
include_graphics(image_path)
```

The [Gravel Tree](qmd/gravel_tree.qmd) page contains a tree diagram showing the relative similarity in frame geometry among all gravel bikes in the database and the clustering of the models into three major styles.

```{r echo=FALSE}
image_folder <- "images"
image_file <- "gravel-tree-1.png"
image_path <- here(image_folder, image_file)
include_graphics(image_path)
```

The [Gravel Table](qmd/gravel_class.qmd) page contains a table of the classification of all gravel bike models in the database into All-road, Endurance, and Trail categories.

```{r echo=FALSE}
image_folder <- "images"
image_file <- "gravel-table.png"
image_path <- here(image_folder, image_file)
include_graphics(image_path)
```

Also, check out the Gravel Stories

[Which gravel bikes have mountain bike inspired geometry?](qmd/which_gravel_bikes_are_mtb_inspired.qmd)

[Is a gravel bike a 1990s mountain bike?](qmd/mtb_90s.qmd)

copyright 2022 Jeffrey A. Walker
