---
title: "Bike Geometry Project"
subtitle: "A project to classify and compare gravel bike geometry"
---

<meta http-equiv="refresh" content="0; URL=https://bikegeometry.site/">
<link rel="canonical" href="https://bikegeometry.site/">

```{r setup-index, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("Rmd", "bike_geometry_project.R")
source(source_path)
```

The [Gravel Scatter](qmd/gravel_scatter.qmd) page contains interactive, 2D scatter plots of different pairs of frame geometry measures for all gravel bike models and frame sizes in the database.

```{r echo=FALSE}
image_folder <- "images"
image_file <- "gravel-scatter.png"
image_path <- here(image_folder, image_file)
include_graphics(image_path)
```

The [Gravel Tree](qmd/gravel_tree.qmd) page contains a tree diagram showing the relative similarity in frame geometry among all gravel bikes in the database and the clustering of the models into three major styles.

```{r echo=FALSE}
image_folder <- "images"
image_file <- "gravel-tree-1.png"
image_path <- here(image_folder, image_file)
include_graphics(image_path)
```

The [Gravel Style](qmd/gravel_class.qmd) page contains a table of the classification of all gravel bike models in the database into All-road, Endurance, and Trail categories.

```{r echo=FALSE}
image_folder <- "images"
image_file <- "gravel-table.png"
image_path <- here(image_folder, image_file)
include_graphics(image_path)
```

Also, check out the Gravel Stories

[Which gravel bikes have mountain bike inspired geometry?](qmd/which_gravel_bikes_are_mtb_inspired.qmd)

[Is a gravel bike a 1990s mountain bike?](qmd/mtb_90s.qmd)

copyright 2022 Jeffrey A. Walker
