---
title: "What can we learn about the functional morphology of bike geometry using geometric morphometrics?"
---

```{r setup-ms}
#| echo: false
#| eval: true
  
# wrangling packages
library(here) # here makes a project transportable
library(janitor) # clean_names
library(readxl) # read excel, duh!
library(openxlsx) # write excel
library(data.table) # magical data frames
library(magrittr) # pipes
library(stringr) # string functions
library(forcats) # factor functions
library(arules) # discretize function

# prediction packages for rider_height
library(glmnet)
library(ranger)
library(xgboost)

# cluster packages
library(ggdendro) # dendrogram
library(dendextend) # better dendrogram
library(bootcluster) # bootstrap dendrogram
library(fpc) # cluster stability
library(mclust) # clustering
library(COveR) # overlapping kmeans
library(ksharp) # sharpen kmeans
library(ktaucenters) # robust kmeans

# graphing packages
library(ggsci) # color palettes
library(ggpubr) # publication quality plots
library(ggforce) # better jitter
library(cowplot) # combine plots
library(knitr) # kable tables
library(kableExtra) # kable_styling tables
library(plotly)

# use here from the here package
here <- here::here
# use clean_names from the janitor package
clean_names <- janitor::clean_names
# use transpose from data.table
transpose <- data.table::transpose

# load functions used by this text written by me
# ggplot_the_model.R needs to be in the folder "R"
# if you didn't download this and add to your R folder in your
# project, then this line will cause an error
#source_path <- here("R", "ggplot_the_model.R")
#source(source_path)

data_folder <- "data"

pal_okabe_ito <- c(
  "#E69F00",
  "#56B4E9",
  "#009E73",
  "#F0E442",
  "#0072B2",
  "#D55E00",
  "#CC79A7"
)

```

# Compute missing measures

```{r deg-2-rad}
deg_2_rad <- function(x){
  rad <- x*pi/180
  return(rad)
}
```

```{r}
compute_offset_h <- function(rake, hta){
  # the horizontal component of fork offset
  offset_h <- rake/sin(deg_2_rad(hta))
  return(offset_h)
}

```

```{r}
compute_head_tube_length <- function(hta, fs, bbd, ac, rake, lhss){
  # head tube angle, frame stack, bb drop, axle crown, lower headset stack
  hta_rad <- hta*pi/180
  beta <- acos(rake/ac)
  delta <- pi/2 - hta_rad
  gamma <- beta - delta
  ac.v <- ac * sin(gamma)
  lhss.v <- lhss * sin(hta_rad)

  h.v <- fs - ac.v - lhss.v - bbd
  htle <- h.v / sin(hta_rad)
  return(htle)
}
```

Steering is the axis from the top of the head tube to the horizontal line through the wheel axles along the head tube angle

```{r compute-steering}
compute_steering_v <- function(fs, bbd){
  # steering_v is the vertical component of the steering axis from top of head tube
  # to the horizontal line through wheel axles - so height from axle to head tube crown
  steering_v <- fs - bbd
  return(steering_v)
}

compute_steering_h <- function(fs, bbd, hta){
  steering_v <- compute_steering_v(fs, bbd)
  steering_h <- steering_v/tan(deg_2_rad(hta))
  return(steering_h)
}
```

```{r compute-wheelbase}
compute_wheelbase <- function(fs, fr, bbd, hta, rake, rc_h){
  # stack, reach, bottom_bracket_drop, head_tube_angle, fork_offset_rake, rear_center_h)
  steering_h <- compute_steering_h(fs, bbd, hta)
  offset_h <- compute_offset_h(rake, hta)
  wb <- rc_h + fr + steering_h + offset_h
  return(wb)
}

```

# Import and Impute

```{r read-geometry}
read_geometry <- function(bike_path,
                          geom_range){
    bike_wide <- read_excel(bike_path,
                          range = geom_range) |>
    data.table()
    bike_wide <- bike_wide[, -2]
    bike <- transpose(bike_wide,
                keep.names = "frame_size",
                make.names = 1)
    return(bike)
}
```

In order to get frame coordinates we need:

1. chainstay length
2. top tube effective length
3. wheelbase
4. front center
5. seat tube angle
6. head tube angle
7. head tube length
8. stack
9. reach
10. bottom bracket drop
11. fork axle-crown
12. fork offset
13. lower crown stack

```{r create-missing-geom-cols}
create_missing_geom_cols <- function(bike_geom){
  measures <- c("chainstay_length", "wheelbase", "front_center", "seat_tube_angle", "head_tube_angle", "head_tube_length", "stack", "reach", "bottom_bracket_drop", "axle_crown", "fork_offset_rake", "lower_headset_stack")
  
  in_measures <- colnames(bike_geom)[-1]
  missing <- setdiff(measures, in_measures)
  for(j in 1:length(missing)){
    bike_geom[, v1 := NA_real_]
    setnames(bike_geom, "v1", missing[j])
  }
  
  bike_geom <- bike_geom[, .SD, .SDcols = c("frame_size", measures)]
  return(bike_geom)
}

```

```{r fill-in-missing-geom}
fill_in_missing_geom <- function(bike){
  measures <- c("chainstay_length", "wheelbase", "front_center", "seat_tube_angle", "head_tube_angle", "head_tube_length", "stack", "reach", "bottom_bracket_drop", "axle_crown", "fork_offset_rake", "lower_headset_stack")

  # headset stack
  bike[is.na(headset_lower) & material == "carbon", lower_headset_stack := 1]
  bike[is.na(headset_lower) & material == "aluminum", lower_headset_stack := 1]
  bike[is.na(headset_lower) & material == "steel", lower_headset_stack := 13]
  bike[is.na(headset_lower) & material == "titanium", lower_headset_stack := 13]
  bike[!is.na(headset_lower) & substr(headset_lower,1,4) == "IS52", lower_headset_stack := 1]
  bike[!is.na(headset_lower) & substr(headset_lower,1,2) == "EC", lower_headset_stack := 13]
  bike[!is.na(headset_lower) & substr(headset_lower,1,2) == "ZS", lower_headset_stack := 3]

  # headtube length
  bike[is.na(head_tube_length), head_tube_length := compute_head_tube_length(head_tube_angle, stack, bottom_bracket_drop, axle_crown, fork_offset_rake, lower_headset_stack)]
  # bike[is.na(head_tube_length), model] |> unique()
  
  # rear_center_h
  bike[, rear_center_h := sqrt(chainstay_length^2 - bottom_bracket_drop^2)]
  
  # wheelbase from front and rear center
  bike[is.na(wheelbase) & !is.na(front_center), # assume bottom_bracket_drop & chainstay_length
          wheelbase := rear_center_h + 
            sqrt(front_center^2 - bottom_bracket_drop^2)]
  
  # wheelbase using fork
  bike[is.na(wheelbase),
          wheelbase := compute_wheelbase(stack, reach, bottom_bracket_drop,
                                         head_tube_angle, fork_offset_rake, rear_center_h)]
  # bike[is.na(wheelbase), model] |> unique()
  
  # front center
  bike[, front_center_h := wheelbase - rear_center_h]

 return(bike)
}
```

```{r}
correct_specs <- function(bike){
  # bike[is.na(tire_width_max_700c), model] |> unique()
  bike[!is.na(tire_width_max_700c) & tire_width_max_700c < 5,
       tire_width_max_700c := as.numeric(tire_width_max_700c) * 25.4]
  bike[!is.na(tire_width_max_650b) & tire_width_max_650b < 5,
       tire_width_max_650b := as.numeric(tire_width_max_650b) * 25.4]
  return(bike)
}
```

```{r}
classify <- function(bike){
  bike[, axle_crown := sqrt((front.x - fork_top.x)^2 + (front.y - fork_top.y)^2)]
  bike[, class := "gravel"]
  bike[axle_crown > 470 & (tire_width_max_700c > 57 | tire_width_max_650b > 57),
       class := "mtb"]
  return(bike)
}
```

```{r import}
#| echo: false
#| eval: true
import_bike_data <- function(){
  file_in <- "gravel"
  filelist_path <- here(data_folder, file_in)
  bike_list <- list.files(filelist_path, pattern = "\\.xlsx$", full.names = FALSE)
  bike_list <- bike_list[!grepl("^~\\$", basename(bike_list))] # delete excel hidden

  n_bikes <- length(bike_list)
  geobike <- data.table(NULL)
  for(i in 1:n_bikes){
    bike_file = bike_list[i]
    bike_path <- here(data_folder, file_in, bike_file)
    model_data <- read_excel(bike_path, range = "A1:B6", col_names = FALSE,
                             .name_repair = "unique_quiet") |>
      data.table()

    model <- transpose(model_data[1:3, 1:2], make.names = 1) |>
      clean_names()
    model[, bike := paste(brand, model, model_year)]

    # read geometry
    geom_range <- read_excel(bike_path, range = "B7:B7",
                             col_names = FALSE,
                             .name_repair = "unique_quiet") |>
      as.character()
    last_row <- substr(geom_range, (nchar(geom_range)-1),
                       nchar(geom_range)) |>
      as.integer()
    bike_geom <- read_geometry(bike_path, geom_range) |>
      data.table()
    bike_geom_clean <- create_missing_geom_cols(bike_geom)
    
    # add model data
    geom_cols <- data.table(
      model,
      bike_geom_clean
    )

    # specs 
    last_row_of_geom <- substr(geom_range, (nchar(geom_range)-1), nchar(geom_range)) |>
      as.integer()
    first_row_of_specs <- last_row_of_geom + 2
    last_row_of_specs <- first_row_of_specs + 100
    specs_range <- paste0("a", first_row_of_specs, ":b", last_row_of_specs)
    bike_specs <- read_excel(bike_path, range = specs_range, col_names = TRUE) |>
      clean_names() |>
      data.table()
    bike_specs <- bike_specs[!apply(is.na(bike_specs), 1, all), ]
    specs_data <- transpose(bike_specs, make.names = 1)
    specs_keep <- c("class", "handlebar", "material", "dropout", "rear_axle", "headset_lower", "tire_width_max_700c", "tire_width_max_650b")
    specs_cols <- specs_data[, .SD, .SDcols = specs_keep]

    # combine
    bike <- cbind(geom_cols, specs_cols)
    geobike <- rbind(geobike, bike)
    
  }
  return(geobike)
}
  
  
```

# Get coordinates

center at rear axle

1. rear axle
2. front axle
3. seat
4. head tube
5. crown
6. bottom bracket

```{r compute-bike-coords}
compute_bike_coords <- function(bike){
  # tan(sta) = setback_v / setback_h 
  bike[, setback_v := stack]
  bike[, setback_h := setback_v /
            tan(deg_2_rad(seat_tube_angle))]
  # sin(hta) = headtube_v / head_tube_length 
  # cos(hta) = headtube_h / head_tube_length 
  bike[, head_tube_v := head_tube_length *
            sin(deg_2_rad(head_tube_angle))]
  bike[, head_tube_h := head_tube_length *
            cos(deg_2_rad(head_tube_angle))]
  bike[, crown_race_v := lower_headset_stack *
            sin(deg_2_rad(head_tube_angle))]
  bike[, crown_race_h := lower_headset_stack *
            cos(deg_2_rad(head_tube_angle))]
  
  bike[, rear.x := 0]
  bike[, rear.y := 0]
  bike[, front.x := wheelbase]
  bike[, front.y := 0]
  bike[, seat.x := rear_center_h - setback_h]
  bike[, seat.y := stack - bottom_bracket_drop]
  bike[, headtube.x := rear_center_h + reach]
  bike[, headtube.y := stack - bottom_bracket_drop]
  bike[, crown.x := headtube.x + head_tube_h]
  bike[, crown.y := headtube.y - head_tube_v]
  bike[, fork_top.x := crown.x + crown_race_h]
  bike[, fork_top.y := crown.y - crown_race_v]
  bike[, bottom_bracket.x := rear_center_h]
  bike[, bottom_bracket.y := -bottom_bracket_drop]
  
  bike[, x1 := rear.x]
  bike[, y1 := rear.y]
  bike[, x2 := front.x]
  bike[, y2 := front.y]
  bike[, x3 := seat.x]
  bike[, y3 := seat.y]
  bike[, x4 := headtube.x]
  bike[, y4 := headtube.y]
  bike[, x5 := crown.x]
  bike[, y5 := crown.y]
  bike[, x6 := bottom_bracket.x]
  bike[, y6 := bottom_bracket.y]
  
  return(bike)
}

```

# morphometrics
## Superimpositions

```{r}
lm_col_labels <- function(p){
  axis_levels <- c("x", "y")
  lm_levels <- 1:p
  lm_cols <- do.call(paste0, expand.grid(axis_levels, lm_levels))
  return(lm_cols)
}

lm_label_names <- function(p){
  axis_levels <- c("x", "y")
  measure_levels <- c("rear", "front", "seat", "headtube", "crown", "bb")
  axis_levels <- paste0(axis_levels, ".")
  lm_cols <- do.call(paste0, expand.grid(axis_levels, measure_levels))
  return(lm_cols)
  
}
```


```{r superimpose-coords}
superimpose_coords <- function(bike){
  lm_cols <- lm_col_labels(6)
  lm_mat <- bike[, .SD, .SDcols = lm_cols] |>
    as.matrix()
  lm_array <- matrix_2_array(lm_mat)
  gg <- plot_shapes(lm_array)
  gg
  
  lm_tpr <- tpr(lm_array, 1, 2)
  gg <- plot_shapes(lm_tpr)
  gg

  lm_ols <- gols(lm_tpr)
  gg <- plot_shapes(lm_ols)
  gg
  
  lm_ols_2 <- gpagen(lm_tpr,
                 PrinAxes = FALSE)$coords
  # rescale
  for(i in 1:dim(lm_ols)[3]){
    y_i <- lm_ols[,,i]
    y_s <- scale_ols(y_i)
    lm_ols_2[,,i] <- y_s
  }
  gg <- plot_shapes(lm_ols)
  gg
  
  lm_grf <- grf(lm_tpr)
  gg <- plot_shapes(lm_grf)
  gg
  
  lm_dt_tpr <- array_2_matrix(lm_tpr) |>
    data.table()
  lm_dt_grf <- array_2_matrix(lm_grf) |>
    data.table()
  lm_dt_ols <- array_2_matrix(lm_ols) |>
    data.table()
  
  colnames(lm_dt_tpr) <- paste0(lm_cols, ".tpr")
  colnames(lm_dt_grf) <- paste0(lm_cols, ".grf")
  colnames(lm_dt_ols) <- paste0(lm_cols, ".ols")  
  
  bike <- cbind(bike, lm_dt_tpr, lm_dt_grf, lm_dt_ols)
  
  return(bike)
}
```

# Bike Means
```{r}
trad_col_labels <- function(){
  trad_cols <- c("rear_center_h", "front_center_h", "setback_h", "reach", "stack", "seat_tube_angle", "head_tube_angle", "bottom_bracket_drop", "axle_crown")
  return(trad_cols)
}

```

```{r}
get_bike_means <- function(bike){
  trad_cols <- trad_col_labels() # returns col names of traditional measures
  lm_labels <- lm_col_labels(6) # returns x1, y1, x2, y2 ...
  lm_cols <- c(paste0(lm_labels, ".tpr"),
                    paste0(lm_labels, ".grf"),
                    paste0(lm_labels, ".ols"))
  measure_cols <- c(trad_cols, lm_cols)

  bike_means <- bike[
    , lapply(.SD, \(x) mean(x, na.rm = TRUE)),
    by = bike,
    .SDcols = measure_cols
  ]
  return(bike_means)
}
```

# Statistics

```{r}
draw_frame <- function(gg, ref_figure, width = 0.3){
  
  cs <- c(ref_figure[1, ], ref_figure[6, ])
  ss <- c(ref_figure[1, ], ref_figure[3, ])
  st <- c(ref_figure[6, ], ref_figure[3, ])
  tt <- c(ref_figure[3, ], ref_figure[4, ])
  ht <- c(ref_figure[4, ], ref_figure[5, ])
  bt <- c(ref_figure[6, ], ref_figure[5, ])
  fk <- c(ref_figure[5, ], ref_figure[2, ])
  segments <- cbind(cs, ss, st, tt, ht, bt, fk) |>
    t()
  colnames(segments) <- c("x", "y", "xend", "yend")
  
  # add bike frame line segments and wheels
  gg <- gg +
    geom_segment(data = segments,
                 aes(x = x, y = y, xend = xend, yend = yend),
                 linewidth = width)
  return(gg)
}
```


```{r pca}
trad_pca <- function(bike){
  trad_cols <- trad_col_labels() # returns col names of traditional measures
  Y <- bike[, .SD, .SDcols = trad_cols] |>
    scale()
  R <- cor(Y)
  S <- cov(Y)
  decomp <- eigen(S)
  E <- decomp$vectors
  L <- decomp$values
  scores <- Y %*% E
  loads <- cor(Y, scores[,1:3])
  
}
```

```{r}
gm_pca <- function(bike,
                    method = "ols",
                    multiple = c(1, 1)){
  
  lm_cols <- lm_col_labels(6)

  n <- nrow(bike)
  p <- length(lm_cols) / 2
  k <- 2
  
  # grf 
  if(method == "grf"){
    measure_cols <- c(paste0(lm_cols, ".grf"))
    Y <- bike[, .SD, .SDcols = measure_cols] |>
      as.matrix()
    colnames(Y) <- lm_label_names(6)
    R <- cor(Y)
    S <- cov(Y)
    decomp <- eigen(S)
    E <- decomp$vectors
    L <- decomp$values
    scores <- Y %*% E
    loads <- cor(Y, scores[,1:3])
  }
  
  # ols
  if(method == "ols"){
    measure_cols <- c(paste0(lm_cols, ".ols"))
    Y <- bike[, .SD, .SDcols = measure_cols] |>
      as.matrix()
    colnames(Y) <- lm_label_names(6)
    R <- cor(Y)
    S <- cov(Y)
    decomp <- eigen(S)
    E <- decomp$vectors
    L <- decomp$values
    L[1:3]/sum(L) * 100
    scores <- Y %*% E
    loads <- cor(Y, scores[,1:3])
    
    coords <- matrix_2_array(Y)
    gpa <- gpagen(coords, PrinAxes = FALSE, print.progress = FALSE)
    # Extract aligned coordinates (shape variables)
    Y_2 <- gpa$coords     # p x k x n aligned coordinates
    plot_shapes(Y_2)
    mean_shape <- mshape(Y_2)
    # Centroid size is available if you later want allometry tests:
    CS <- gpa$Csize
    # 3) PCA on Procrustes shape coordinates (tangent space)
    # gm.prcomp is geomorph's standard PCA for aligned landmark coordinates.
    pca <- gm.prcomp(Y_2)
    # Scores for specimens (n x PCs)
    scores_2 <- pca$x
    cor(cbind(scores[,1:3], scores_2[,1:3]))
    loads_2 <- cor(Y, scores_2[,1:3])
    data.table(
      pc1_1 = loads[,1],
      pc1_2 = loads_2[,1]
    )
  }
  
  colnames(scores) <- paste0("pc_", 1:ncol(E))
  colnames(loads) <- paste0("pc_", 1:3)

  gg_dat <- bike[, .SD, .SDcols = c("bike", "class")]
  gg_dat <- data.table(
    bike[, .SD, .SDcols = c("bike", "class")],
    scores[, 1:2]
  )

  b1 <- lm(Y ~ scores[, 1])$coef |>
    t()
  score_1_hi <- c(1, max(scores[, 1]))
  score_1_lo <- c(1, min(scores[, 1]))
  pc1_hi <- b1 %*% score_1_hi
  pc1_lo <- b1 %*% score_1_lo
  pc1 <- cbind(pc1_lo, pc1_hi) |> t()
  rownames(pc1) <- c("pc1_lo", "pc1_hi")
  pc1_figs <- matrix_2_array(pc1)
  gg1_hi <- ggtps(pc1_figs[,,2], pc1_figs[,,1],
                  multiple = multiple[1]) |>
    draw_frame(ref_figure = pc1_figs[,,2], width = 1)
  gg1_lo <- ggtps(pc1_figs[,,1], pc1_figs[,,2],
                  multiple = multiple[1]) |>
    draw_frame(ref_figure = pc1_figs[,,1], width = 1)
  
  gg_pc1 <- plot_difference_vectors(
    ref_fig = matrix_2_vector(pc1_figs[,,1]),
    target_fig = matrix_2_vector(pc1_figs[,,2]),
    mag = multiple[1]) |>
    draw_frame(ref_figure = pc1_figs[,,1], width = 1)
  
  b2 <- lm(Y ~ scores[, 2])$coef |>
    t()
  score_2_hi <- c(1, max(scores[, 2]))
  score_2_lo <- c(1, min(scores[, 2]))
  pc2_hi <- b2 %*% score_2_hi
  pc2_lo <- b2 %*% score_2_lo
  pc2 <- cbind(pc2_lo, pc2_hi) |> t()
  rownames(pc2) <- c("pc2_lo", "pc2_hi")
  pc2_figs <- matrix_2_array(pc2)
  gg2_hi <- ggtps(pc2_figs[,,2], pc2_figs[,,1],
                  multiple = multiple[2]) |>
    draw_frame(ref_figure = pc2_figs[,,2], width = 1)
  gg2_lo <- ggtps(pc2_figs[,,1], pc2_figs[,,2],
                  multiple = multiple[2]) |>
    draw_frame(ref_figure = pc2_figs[,,1], width = 1)
  
  gg_pc2 <- plot_difference_vectors(
    ref_fig = matrix_2_vector(pc2_figs[,,1]),
    target_fig = matrix_2_vector(pc2_figs[,,2]),
    mag = multiple[2]) |>
    draw_frame(ref_figure = pc2_figs[,,1], width = 1)
  
  gg_tps <- plot_grid(gg1_hi, gg1_lo, gg2_hi, gg2_lo,
            ncol = 2, labels = c("PC1", "", "PC2", ""))
  gg_pca <- plot_grid(gg_pc1, gg_pc2,
            ncol = 2, labels = c("PC1","PC2"))
  
  gg_scatter <- ggplot(data = gg_dat,
                aes(x = pc_1,
                    y = pc_2,
                    color = class)) +
    geom_point()
  
  gg_plotly <- plot_ly(
    data = gg_dat,
    x = ~pc_1,
    y = ~pc_2,
    type = 'scatter',
    mode = 'markers',
    color = ~class,
    text = ~bike,
    hoverinfo = "text" # Tells Plotly to use the 'text' column for all hover info
  )
  
  # PCA TPS using standard tools
  mult <- 4
  pc_index <- 1
  # SD of PC scores (using sample SD)
  pc_sd <- sd(scores[, pc_index])
  # Mean shape vector (length p*k)
  mu <- pca$center
  # Loading vector for that PC (length p*k)
  v  <- pca$rotation[, pc_index]
  # Target shapes as vectors in tangent space
  vec_minus <- mu + v * (-mult * pc_sd)
  vec_plus  <- mu + v * (+mult * pc_sd)
  # Convert vectors back to p x k matrices
  target_minus <- matrix(vec_minus, nrow = p, ncol = k, byrow = TRUE)
  target_plus  <- matrix(vec_plus,  nrow = p, ncol = k, byrow = TRUE)
  mean_shape <- matrix(mu, nrow = p, ncol = k, byrow = TRUE)
  par(mfrow = c(1,2))
  plotRefToTarget(mean_shape, target_minus, method = "TPS",
                  main = paste0("PC", pc_index, " -", mult, " SD"))
  plotRefToTarget(mean_shape, target_plus, method = "TPS",
                  main = paste0("PC", pc_index, " +", mult, " SD"))
  par(mfrow = c(1,1))
  
  
  return(list(L, scores, loads, gg_tps, gg_scatter, gg_plotly, gg_pca))
}
```


# simulate pinochio with TPS

TPS is a model of superimposition. Interpreting a TPS is no different than interpreting difference vectors.

```{r tps-ols}
fig_a <- c(c(0, 0),
           c(1, 0),
           c(0, 1),
           c(1, 1),
           c(3, 0.5))
fig_b <- c(c(0, 0),
           c(1, 0),
           c(0, 1),
           c(1, 1),
           c(4, 0.5))
# OLS
figs <- rbind(fig_a, fig_b)
figs_array <- matrix_2_array(figs)
lm_ols_0 <- ols(figs_array, ref = 1)
lm_ols_1 <- gols(figs_array)
lm_ols_2 <- gpagen(figs_array,
                 PrinAxes = FALSE)$coords
# rescale
for(i in 1:dim(lm_ols_2)[3]){
  y_i <- lm_ols_2[,,i]
  y_s <- scale_ols(y_i)
  lm_ols_2[,,i] <- y_s
}
gg <- plot_shapes(lm_ols_2)
gg

# TPS
mat_a.1 <- matrix(t(fig_a), nrow= 2) |> t()
mat_b.1 <- matrix(t(fig_b), nrow= 2) |> t()
tps(mat_b.1, mat_a.1, gridlines = 20,
    multiple = 1)

```


```{r tps-many-box-points}
# box_1 is a simple box with landmarks at four corners
box_1 <- c(c(0, 0),
         c(1, 0),
         c(0, 1),
         c(1, 1)
)

# box_2 is the same box but has a grid of landmarks
make_unit_landmarks_dt <- function(p) {
  stopifnot(length(p) == 1L, is.numeric(p), p >= 2)

  vals <- seq(0, 1, length.out = p)

  xy <- CJ(x = vals, y = vals)   # cartesian join
  as.matrix(xy)
}

box_2 <- make_unit_landmarks_dt(11)

box1_mat <- matrix(t(box_1), nrow= 2) |> t()
box2_mat <- matrix(t(box_2), nrow= 2) |> t()

fig1.ref <- rbind(box1_mat, c(1.5, 0.5))
fig1.target <- rbind(box1_mat, c(2.5, 0.5))
fig2.ref <- rbind(box2_mat, c(1.5, 0.5))
fig2.target <- rbind(box2_mat, c(2.5, 0.5))


ggtps(fig1.target, fig1.ref, gridlines = 30,
    multiple = 1)
ggtps(fig2.target, fig2.ref, gridlines = 30,
    multiple = 1)

```

1. A TPS deforms the entire space
2. The deformation minimizes the bending energy.
3. Can we think of this as, the TPS superimposes the figure in a way that minimizes bending energy?
4. The deformation looks similar to how we'd imagine the deformation to be if we mentally deform the space after the OLS superimposition.
5. The GRF superimposition implies a very different deformation.


# Run Everything

```{r run-everything}
import_it <- FALSE
if(import_it){
  geobike_all <- import_bike_data()
  geobike_import <- copy(geobike_all)
}else{
  geobike_all <- copy(geobike_import)
}
geobike_all <- geobike_all |>
  fill_in_missing_geom() |>
  correct_specs() |>
  compute_bike_coords() |>
  classify() |>
  superimpose_coords()
  
geobike <- geobike_all |>
  get_bike_means()
geobike_bike_cols <- geobike_all[, 
                                 .(x1.tpr = mean(x1.tpr)),
                                 by = .(bike, class, handlebar)]
geobike <- merge(geobike_bike_cols[, .SD, .SDcols = c("bike", "class", "handlebar")],
                 geobike, by = "bike")

# all bikes
pca_ols <- gm_pca(geobike, method = "ols", multiple = c(1.5, 3))
# list(L, scores, loads, gg1, gg3, p3)
pca_ols_vals <- pca_ols[[1]]
pca_ols_loads <- pca_ols[[3]]
pca_ols_gg_tps <- pca_ols[[4]]
pca_ols_scatter <- pca_ols[[5]]
pca_ols_plotly <- pca_ols[[6]]

pca_ols_vals
pca_ols_loads
pca_ols_gg_tps
pca_ols_scatter
pca_ols_plotly

# drop bar bikes
pca_ols <- gm_pca(geobike[handlebar == "drop bar" | handlebar == "both"],
                  method = "ols",
                  multiple <- c(1.5, 2))
pca_ols_vals <- pca_ols[[1]]
pca_ols_loads <- pca_ols[[3]]
pca_ols_gg_tps <- pca_ols[[4]]
pca_ols_scatter <- pca_ols[[5]]
pca_ols_plotly <- pca_ols[[6]]
pca_ols_gg_pca <- pca_ols[[7]]

pca_grf <- gm_pca(geobike[handlebar == "drop bar" | handlebar == "both"],
                  method = "grf",
                  multiple <- c(1.5, 2))
pca_grf_vals <- pca_grf[[1]]
pca_grf_loads <- pca_grf[[3]]
pca_grf_gg_tps <- pca_grf[[4]]
pca_grf_scatter <- pca_grf[[5]]
pca_grf_plotly <- pca_grf[[6]]
pca_grf_gg_pca <- pca_grf[[7]]


```


```{r pca-ols-loads}
pca_ols_vals[1:3]/sum(pca_ols_vals)
pca_ols_loads

```

Loadings interpretation

1. PC1: positive PC1 correlated with 1) long fork, 2) shallow fork angle (increased fork offset), 3) steeper head tube, 4) shorter head tube because longer fork, 5) steeper seat tube angle -> shorter top tube 6) shorter rear center, 7) higher bottom bracket
2. PC2: positive PC2 correlated with 1) higher seat/head tube -> stack, short front center 3) short wheelbase, 4) short reach due to head tube moving toward seat, 5) slacker head tube angle
3. PC3: 1) short front center, 2) long rear center, 3) steeper head tube angle

```{r pca-ols-gg-pca}
pca_ols_gg_pca
```

1. Positive PC1: shorter/steeper head tube, longer/slacker fork
2. Positive PC2: higher stack, longer head tube, steeper fork, shorter front center, a big longer rear center but overall shorter wheelbase.

```{r pca-ols-gg-tps}
pca_ols_gg_tps
```

The PCA figures were computed using PCA of OLS coords so the TPS is approximate since minimizing bending energy and least squares are not the same.

Notes:

1. Positive TPS1: short, steep headtube, long? fork with steep fork angle (short fork offset), short rear center, short front center (due to short fork offset), short top tube that steepens the seat tube, high bottom bracket
2. Positive TPS2: higher stack, long, steep head tube, short steep fork


```{r pca-ols-plotly}
pca_ols_plotly
```

1. Positive TPS1: short, steep headtube, long? fork with steep fork angle (short fork offset), short rear center, short front center (due to short fork offset), short top tube that steepens the seat tube, high bottom bracket
2. Positive TPS2: higher stack, long, steep head tube, short steep fork
