---
params:
  brand: ~
  model: ~
  year: ~
  slug: ~
  data_path: ~
  site_base_url: ~
---

```{r setup, include=FALSE}
library(data.table)
library(jsonlite)
library(knitr)

# Safe accessor: read from params without writing to it
get_param <- function(nm, default = NULL) {
  v <- tryCatch(params[[nm]], error = function(e) NULL)
  if (is.null(v) || is.na(v) || !nzchar(as.character(v))) return(default)
  as.character(v)
}

# Pull values (do NOT assign into `params`)
brand_val <- get_param("brand",         Sys.getenv("BRAND",         "DEBUG_BRAND"))
model_val <- get_param("model",         Sys.getenv("MODEL",         "DEBUG_MODEL"))
year_val  <- get_param("year",          Sys.getenv("YEAR",          "DEBUG_YEAR"))
slug_val  <- get_param("slug",          Sys.getenv("SLUG",          "debug-slug"))
data_path <- get_param("data_path",     Sys.getenv("DATA_PATH",     "data/geobike.rds"))
site_base <- get_param("site_base_url", Sys.getenv("SITE_BASE_URL", "https://example.com"))

# Load data
if (!file.exists(data_path)) {
  stop("RDS not found at: ", data_path, "\n(getwd() during render: ", getwd(), ")")
}
geobike <- readRDS(data_path)
if (!is.data.table(geobike)) setDT(geobike)

bike <- geobike[
  brand == brand_val &
  model_name == model_val &
  year  == year_val
]

if (nrow(bike) == 0) {
  stop(sprintf(
    "No rows found for brand='%s' model='%s' year='%s' (lookup uses columns brand / model_name / year).",
    brand_val, model_val, year_val
  ))
}

# SEO bits
page_title   <- sprintf("%s %s %s", brand_val, model_val, year_val)
page_desc    <- sprintf("Geometry, specs, and sizing for the %s %s (%s) gravel bike.", brand_val, model_val, year_val)
canonical_url<- sprintf("%s/bikes/%s.html", site_base, slug_val)
img_url      <- if ("image_url" %in% names(bike)) bike[1, image_url] else NA_character_

```

```{r meta, echo=FALSE, results='asis'}
# Emit canonical + meta description as literal HTML (safe, minimal)
cat(sprintf('<link rel="canonical" href="%s">\n', canonical_url))
cat(sprintf('<meta name="description" content="%s">\n', page_desc))
# Also set browser title so tab shows the SEO title
cat(sprintf('<script>document.title=%s;</script>\n', toJSON(page_title, auto_unbox=TRUE)))
```

**Brand:** `r params$brand`\
**Model:** `r params$model`\
**Year:** `r params$year`\
**Category:** `r bike[1, class]`\
**Similar bikes:** `r bike[1, similar_bikes]`

```{r hero, echo=FALSE, results='asis'}
if (!is.na(img_url) && nzchar(img_url)) {
  cat(sprintf(
    '<img src="%s" alt="%s %s %s" style="max-width:720px;width:100%%;border-radius:12px;margin:1rem 0;">',
    img_url, params$brand, params$model, params$year
  ))
}
```

## Geometry & Specs

```{r table, echo=FALSE}
options(knitr.kable.NA = '')
# spec columns present in geobike
specs_cols <- c("frame_size","estimated_rider_height", "specified_rider_height", "kmeans_style", "material", "fork", "handlebar", "top_tube_effective_length_est", "reach", "stack", "standover", "head_tube_angle", "seat_tube_angle","chainstay_length", "front_center", "bottom_bracket_drop", "trail", "trail_45", "udh", "tire_width_max_700c", "tire_width_max_650b", "fork_class", "axle_spacing", "stealth_dropper", "seatpost_diameter", "max_chainring_1x", "dropout", "internal_storage", "base_build_usd", "frameset_usd", "location")
keep_cols <- intersect(specs_cols, names(bike))

# Order by numeric size where possible

kb <- bike[, ..keep_cols]
kb <- kb[order(reach)]

setnames(
  kb,
  old = c("kmeans_style", "fork_class", "top_tube_effective_length_est"),
  new = c("style", "suspension_correction", "effective_top_tube_length")
)

# Rounding / currency
kb[, front_center := round(front_center, 0)]
kb[, trail := round(trail, 0)]
kb[, trail_45 := round(trail_45, 0)]
kb[, frameset_usd := ifelse(is.na(frameset_usd), frameset_usd, paste0("$", round(frameset_usd, 0)))]
kb[, base_build_usd := ifelse(is.na(base_build_usd), base_build_usd, paste0("$", round(base_build_usd,0)))]

kb <- t(kb)
spec_col <- rownames(kb)
spec_col <- stringr::str_replace_all(spec_col, "_", " ")
spec_col <- stringr::str_to_title(spec_col)
spec_col <- stringr::str_replace(spec_col, "Udh", "UDH")
spec_col <- stringr::str_replace(spec_col, "Usd", "USD")
rownames(kb) <- spec_col

kable(kb, format = "html", table.attr = 'class="table table-sm table-striped"') |>
  kableExtra::kable_styling()
```


```{r jsonld, echo=FALSE, results='asis'}
first_row <- if (nrow(kb)) as.list(kb[1]) else list()
props <- lapply(names(first_row), function(nm) {
  list(`@type`="PropertyValue", name=nm, value=as.character(first_row[[nm]]))
})

schema <- list(
  `@context` = "https://schema.org",
  `@type`    = "Product",
  name       = sprintf("%s %s %s", params$brand, params$model, params$year),
  brand      = list(`@type`="Brand", name=params$brand),
  category   = "Bicycle",
  productID  = paste(params$brand, params$model, params$year),
  url        = canonical_url,
  image      = if (is.na(img_url) || !nzchar(img_url)) NULL else img_url,
  description= page_desc,
  additionalProperty = props
)

cat('<script type="application/ld+json">')
cat(toJSON(schema, auto_unbox = TRUE, null = "null"))
cat('</script>')
```

### Related

See where the `r params$brand` `r params$model` `r params$year` fits into 
<a href="/qmd/gravelverse.html">The GravelVerse</a>, 
a plot that compares overall similarity of frame geometry among gravel bikes.

<a href="/qmd/gravel_compare.html">Compare three other bikes</a> to the `r params$brand` `r params$model` `r params$year` on key frame specs and frame geometry measures.

<a href="/qmd/gravel_sus_table.html">See how the geometry changes</a> if you add a suspension fork to the `r params$brand` `r params$model` `r params$year`.

**Internal Links:**\
- [All bikes index](/bikes/bike_index.html)\
- [Home](/)
