---
title: "How does a suspension fork change bike geometry -- Plots of data"
---

::: {.callout-tip title="Tips for navigating"}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model.
3. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-tip title="More notes!"}
More notes at the bottom!
:::

```{r setup-gravel-scatter, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```


```{r make-plots, echo=FALSE}
#geobike_sus_shared <- SharedData$new(geobike_sus[my_fit == TRUE,], key = ~model_size, group = "2dsus")
geobike_sus_shared <- SharedData$new(geobike_sus[my_fit == TRUE,], key = ~row_id, group = "2dsus")

p1 <- scatter_fig(shared_data = geobike_sus_shared,
                  link_group = "2dsus",
                  x_col = "reach", y_col = "stack",
                  x_label = "Reach (mm)", y_label = "Stack (mm)",
                  g_col = "model_size",
                  filter_col = "fork_key",
                  filter_keep = "rigid",
                  label_col = "label",
                  xtra_info = "fork",
                  same_xy_scale = FALSE)
p2 <- scatter_fig(shared_data = geobike_sus_shared,
                  link_group = "2dsus",
                  x_col = "seat_tube_angle", y_col = "head_tube_angle",
                  x_label = "Seat Tube Angle (°)", y_label = "Head Tube Angle (°)",
                  x_info = "STA", y_info = "HTA", digits = 1,
                  g_col = "model_size",
                  filter_col = "fork_key",
                  filter_keep = "rigid",
                  label_col = "label",
                  xtra_info = "fork",
                  same_xy_scale = FALSE)
p3 <- scatter_fig(shared_data = geobike_sus_shared,
                  link_group = "2dsus",
                  x_col = "bottom_bracket_drop", y_col = "trail_45",
                  x_label = "Bottom Bracket Drop (mm)", y_label = "Trail (45 mm tire) (mm)",
                  x_info = "BB drop", y_info = "Trail-45", digits = 1,
                  g_col = "model_size",
                  filter_col = "fork_key",
                  filter_keep = "rigid",
                  label_col = "label",
                  xtra_info = "fork",
                  same_xy_scale = FALSE)
p4 <- scatter_fig(shared_data = geobike_sus_shared,
                  link_group = "2dsus",
                  x_col = "front_center", y_col = "rear_center",
                  x_label = "Front Center (H) (mm)", y_label = "Rear Center (H) (mm)",
                  x_info = "FC", y_info = "RC", digits = 1,
                  g_col = "model_size",
                  filter_col = "fork_key",
                  filter_keep = "rigid",
                  label_col = "label",
                  xtra_info = "fork",
                  same_xy_scale = FALSE)




```


```{r, echo = FALSE, out.height="100%", out.width="100%"}
# set up check boxes

  # gg_legend_ly <- ggplotly(gg_legend, width = 6.5*96, height = 1*96)

  boxes <- filter_checkbox("fork", "Fork", geobike_sus_shared, ~travel, inline = FALSE)
  bscols(widths = c(8,3), p1, boxes)
  bscols( widths = c(8,3), p2)
  bscols( widths = c(8,3), p3)
  bscols( widths = c(8,3), p4)

  # p3
  # p4
  # p5
  # p6
  # p7
  # p8
  # p9

```




::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 175 cm high rider (generally frame size M or 54), according to manufacturer's charts.
:::

::: {.callout-note}
The suspension fork length and geometry is based on 20% sag: fork_length - 0.2*travel
:::

::: {.callout-warning title="A Rudy Fork geometry corrector"}
Rockshox recommends 5% sag on the Rudy fork while Fox, Cane Creek, and Lauf recommend (or are tuned for) 20% sag. The sus geometry for a 30 mm Rudy fork will be about 1/2 way between the 30 mm and 40 mm measures (for the same offset). The sus geometry for a 40 mm Rudy fork will be about 3/5 way between the 40 mm and 50 mm measures (for the same offset).
:::

::: {.callout-warning title="Is your frame suspension corrected?"}
Several companies are calling their frame suspension corrected, or sell a suspension fork with a build, but their rigid Axle-Crown length is far short (by > 10 mm and often > 15 mm) the sagged length of a 30 mm fork.
:::

::: {.callout-tip title="Gravel forks"}
1. Cane Creek Invert has two models: 30 mm (425 mm axle-crown) and 40 (435 mm axle-crown) mm travel. Both models have 45 mm offset
2. Rockshox Rudy has four models: 30 mm (425 mm axle-crown) and 40 (435 mm axle-crown) mm travel, each with either 45 mm or 51 mm offset.
3. Fox 32 TC Factory has four models: 40 (435.5 mm axle-crown) mm and 50 (445.5 mm axle-crown) mm travel, each with either 45 mm or 50 mm offset.
4. Lauf has one model with 30 mm travel (425 Axle Crown and 47 mm offset)
:::


