---
title: "What makes a rowdy frame rowdy?"
editor: source
format:
  html:
    toc: false
---
::: {.callout-tip}
1. Hover over data for model and frame size identification.
2. Scroll legend and click on items to identify specific model and frame size combinations.
3. Click on popup icon-bar over legend to zoom in/out and pan.
:::

::: {.callout-note}
Classification of gravel bikes is based on a frame size that fits a 175 cm high rider (generally frame size M or 54), according to manufacturer's charts.
:::

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
source_path <- here::here("bike_geometry_project.R")
source(source_path)
```


```{r make-plots, echo=FALSE}

rowdy_shared <- SharedData$new(geobike[my_fit == TRUE],
                                 key = ~model_size, group = "2drowdy")
add_regression <- TRUE

# which classifier
tree_class <- 1
functional_class <- 2
kmeans_class <- 3
mclust_class <- 4
rowdy_col <- c("tree_rowdy", "functional_rowdy", "kmeans_rowdy", "mclust_rowdy")[kmeans_class]
color_col <- c("tree_style", "functional_style", "kmeans_style", "mclust_style")[kmeans_class]

p1 <- scatter_fig(shared_data = rowdy_shared,
                  link_group = "2drowdy",
                  y_col = rowdy_col, x_col = "stack",
                  y_label = "Rowdy Index", x_label = "Stack (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p2 <- scatter_fig(shared_data = rowdy_shared,
                  link_group = "2drowdy",
                  y_col = rowdy_col, x_col = "reach",
                  y_label = "Rowdy Index", x_label = "Reach (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p3 <- scatter_fig(shared_data = rowdy_shared,
                  link_group = "2drowdy",
                  y_col = rowdy_col, x_col = "head_tube_angle",
                  y_label = "Rowdy Index", x_label = "Head Tube Angle (°)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p4 <- scatter_fig(shared_data = rowdy_shared,
                  link_group = "2drowdy",
                  y_col = rowdy_col, x_col = "seat_tube_angle",
                  y_label = "Rowdy Index", x_label = "Seat Tube Angle (°)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p5 <- scatter_fig(shared_data = rowdy_shared,
                  link_group = "2drowdy",
                  y_col = rowdy_col, x_col = "bottom_bracket_drop",
                  y_label = "Rowdy Index", x_label = "Bottom Bracket Drop (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p6 <- scatter_fig(shared_data = rowdy_shared,
                  link_group = "2drowdy",
                  y_col = rowdy_col, x_col = "chainstay_length",
                  y_label = "Rowdy Index", x_label = "Chainstay Length (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p7 <- scatter_fig(shared_data = rowdy_shared,
                  link_group = "2drowdy",
                  y_col = rowdy_col, x_col = "front_center",
                  y_label = "Rowdy Index", x_label = "Front Center (mm)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p8 <- scatter_fig(shared_data = rowdy_shared,
                  link_group = "2drowdy",
                  y_col = rowdy_col, x_col = "stack_reach",
                  y_label = "Rowdy Index", x_label = "Stack:Reach",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p9 <- scatter_fig(shared_data = rowdy_shared,
                  link_group = "2drowdy",
                  y_col = rowdy_col, x_col = "front_rear",
                  y_label = "Rowdy Index", x_label = "Front Center:Rear Center",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)
p10 <- scatter_fig(shared_data = rowdy_shared,
                  link_group = "2drowdy",
                  y_col = rowdy_col, x_col = "trail_45",
                  y_label = "Rowdy Index", x_label = "Trail (mm) (with 45mm tire)",
                  g_col = "model_size",
                  color_col = color_col,
                  same_xy_scale = FALSE,
                  add_regression = add_regression)


```



### Rowdy frames have long front ends, slack headtube angles and high trail

```{r rowdy-high, echo=FALSE, message=FALSE, warning=FALSE, out.height="100%", out.width="70%"}
# boxes

p2
p3
p7
p9
p10

```

### Stack, seattube angle, bottom bracket drop, and chainstay length aren't really related to rowdiness

```{r rowdy-low, echo=FALSE, message=FALSE, warning=FALSE, out.height="100%", out.width="70%"}
# boxes
p1
p4
p5
p6
p8

```


